---
title: "midterm project team 5"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Install some packages or libraries
```{r}
library(ggplot2)
library(ezids)
library(dplyr)
library(readr)
library(tidyr)
library(lubridate)
library(knitr)
library(magrittr)
```

### Read data
Read the data .CSV files of adults arrest in DC area from 2016-2021
```{r }
df_2016<-data.frame(read.csv("Arrests 2016 Public.csv"))
df_2017<-data.frame(read.csv("Arrests 2017 Public.csv"))
df_2018<-data.frame(read.csv("Arrests by Year, 2018.csv"))
df_2019<-data.frame(read.csv("Arrests by Year, 2019.csv"))
df_2020<-data.frame(read.csv("Arrests by Year 2020.csv"))
df_2021<-data.frame(read.csv("2021 Adult Arrests.csv"))
```


### Some data cleaning.. Dropping, Binding and Renaming of columns as needed.
```{r}

#bind the rows in the dataframes; 
# data for year 2016 & 2017 have different column listings to the rest of the dataframes..

colnames(df_2016) = colnames(df_2017)
df_16_17 = rbind(df_2016,df_2017)

#also remove certain hard-coded columns that are not really needed in this analysis (leaving district location for now)
df_16_17 = df_16_17[-c(5,6,15,17:21,23:26)]
df_16_17 <- df_16_17 %>% 
       rename("Offense.Location.District" = "Offense.District")

# replace dots with underscore for clarity sake, i think..
names(df_16_17) = gsub("[.]", "_", names(df_16_17))
#colnames(df_16_17)

```

```{r}
# since col names in 2018-2021 are the same, we repeat same processes as above.
df_18_21 = rbind(df_2018,df_2019,df_2020,df_2021)[,-c(5,6,15,17:21,23:26)]

# replace dots with underscore once more
names(df_18_21) = gsub("[.]", "_", names(df_18_21))
#colnames(df_18_21)

```

```{r}
#Now bind both newly created dataframes into 1 whole table.
df_full = rbind(df_16_17,df_18_21)
#check for column names
colnames(df_full)

```

```{r}
#find unique values in the race, sex and arrest_category columns.
#unique(df_full$Defendant_Race)
#unique(df_full$Defendant_Sex)
#unique(df_full$Arrest_Category)

# most likely "UNK" is the same as "Unknown", so we can change this
df_full$Defendant_Race[df_full$Defendant_Race == 'UNK'] <- 'UNKNOWN'
#unique(df_full$Defendant_Race) - check that it changed

#same issue, "unk" is very likely "unknown", so change it.
df_full$Defendant_Sex[df_full$Defendant_Sex == 'UNK'] <- 'UNKNOWN'
#unique(df_full$Defendant_Sex) - check that it changed

# Arrest category -  4 different types of Fraud & Financial crimes , 3 types of Release Violations/Fugitive -- group them into one.

df_full$Arrest_Category = gsub("Fraud and Financial Crimes.*","Fraud and Financial Crimes", df_full$Arrest_Category)

df_full$Arrest_Category = gsub("Release Violations/Fugitive.*","Release Violations/Fugitive",df_full$Arrest_Category)

#sort(unique(df_full$Arrest_Category)) - check that new changes were made.
```

### Missing Values
```{r}
sapply(df_full, function(x) sum(is.na(x)))
```
##### Our variables of concern in thsi dataset contain rich data.. over 95% of data available in each useful column.. will not delete any rows


```{r}
#get month and day variables.. might be interesting, who knows?
df_full <- separate(df_full, col = Arrest_Date, into = c("Year","Month","Day"), sep = "-", remove = FALSE, fill="left")
#remove the new year column formed, it is redundant.. we already have Year column
df_full = df_full[,-4]
colnames(df_full)
```


```{r}
# Factorize some variables
df_full$Arrest_Year = as.factor(df_full$Arrest_Year)
df_full$Month = as.factor(df_full$Month)
df_full$Day = as.factor(df_full$Day)
df_full$Defendant_Race = as.factor(df_full$Defendant_Race)
df_full$Defendant_Sex = as.factor(df_full$Defendant_Sex)
df_full$Arrest_Location_District = as.factor(df_full$Arrest_Location_District)
df_full$Offense_Location_District = as.factor(df_full$Offense_Location_District)
# convert to date format
df_full$Arrest_Date = as.Date(df_full$Arrest_Date)
# Day format
df_full$Day = day(df_full$Arrest_Date)
# i want to create a week-day variable
df_full$Weekday = weekdays(df_full$Arrest_Date)
df_full$Weekday = factor(df_full$Weekday, levels = as.character(wday(c(2:7,1), label=TRUE, abbr=FALSE)))

# convert crime types to factors
df_full$Arrest_Category = as.factor(df_full$Arrest_Category)
```

# EDA (?)

### Daily Crime Trend (2016-2021)

```{r echo=FALSE, warning=FALSE, fig.width=8, fig.height=5.5}

by_date <- df_full %>% group_by(Arrest_Date) %>% dplyr::summarise(Total = n())
ggplot(by_date, aes(Arrest_Date, Total, color = Arrest_Date)) + 
  geom_line() 
  #geom_vline(xintercept = "2020-03-11")

```


### All Crimes By Hour, Day, Month, Year


#### Hour of the day.. at what time do these crimes occur the most?

```{r}
by_hour <- df_full %>% 
           group_by(Arrest_Hour) %>% 
           dplyr::summarise(Total = n())
by_hour

ggplot(by_hour, aes(Arrest_Hour, Total, color = Arrest_Hour)) + 
    geom_line() + 
    ggtitle("Crimes By Hour") + 
    xlab("Hour of the Day") + 
    ylab("Total Crimes") 
```


#### Day  .. What day of the month has the highest crime incidents?
```{r}
by_day <- df_full %>% 
           group_by(Day) %>% 
           dplyr::summarise(Total = n())
by_day

ggplot(by_day, aes(Day, Total, color = Day)) + 
    geom_line() + 
    ggtitle("Crimes By Day") + 
    xlab("Day of the Month") + 
    ylab("Total Crimes")
```

#### Day of the week..
```{r}
by_weekday = df_full %>% group_by(Weekday) %>% 
           dplyr::summarise(Total = n())
by_weekday$Percent <- by_weekday$Total/dim(df_full)[1] * 100
by_weekday

ggplot(by_weekday, aes(Weekday, Total, fill = Weekday)) + 
      geom_bar(stat = "identity") +
      ggtitle("Crimes By Weekday ") + 
      xlab("Day of the Week") + ylab("Count") + 
      theme(legend.position = "none")
```

#### Monthly crime incidence
```{r}
by_month <- df_full %>% 
            group_by(Month) %>% 
            dplyr::summarise(Total = n())

by_month$Percent <- by_month$Total/dim(df_full)[1] * 100
by_month

ggplot(by_month, aes(Month, Total, fill = Month)) + 
        geom_bar(stat = "identity") + 
        ggtitle("Crimes By Month") + 
        xlab("Month") + 
        ylab("Count") + 
        theme(legend.position = "none")

ggplot(by_month, aes(x=Month, y=Total, group=1)) + geom_line()
```



####Crime incidence grouped into yearly plots..
```{r}
by_year = df_full %>% group_by(Arrest_Year) %>% 
           dplyr::summarise(Total = n())
by_year$Percent <- by_year$Total/dim(df_full)[1] * 100
by_year

ggplot(by_year, aes(Arrest_Year, Total, fill = Arrest_Year)) + 
      geom_bar(stat = "identity") +
      ggtitle("Crimes By Year ") + 
      xlab("Year") + ylab("Count") + 
      theme(legend.position = "none")

ggplot(by_year, aes(x=Arrest_Year, y=Total, group=1)) + geom_line()
```



## Time to investigate our main focus group - White Males - EDA

```{r}
#unique(df_full$Defendant_Race)
#table(df_full$Defendant_Sex)
df_wm = subset(df_full, subset = Defendant_Race == "WHITE" & Defendant_Sex == "MALE")
head(df_wm, 20)

# i want to create a week-day variable
df_wm$Weekday = weekdays(df_wm$Arrest_Date)
df_wm$Weekday = factor(df_wm$Weekday, levels = as.character(wday(c(2:7,1), label=TRUE, abbr=FALSE)))
```

same pattern here as above, will dig into a few other stuff too..

#### White Men - By the Hour
```{r}
wm_by_hour <- df_wm %>% 
           group_by(Arrest_Hour) %>% 
           dplyr::summarise(Total = n())
wm_by_hour

ggplot(wm_by_hour, aes(Arrest_Hour, Total, color = Arrest_Hour)) + 
    geom_line() + 
    ggtitle("White Males - Crimes By Hour") + 
    xlab("Hour of the Day") + 
    ylab("Total Crimes")
```


#### White Men - What day of the month has the highest crime incidents?
```{r}
wm_by_day <- df_wm %>% 
           group_by(Day) %>% 
           dplyr::summarise(Total = n())
wm_by_day

ggplot(wm_by_day, aes(Day, Total, color = Day)) + 
    geom_line() + 
    ggtitle("White Males - Crimes By Day") + 
    xlab("Day of the Month") + 
    ylab("Total Crimes")
```

#### White Men - What Day of the Week has the highest crime incidents?
```{r}
wm_by_weekday = df_wm %>% group_by(Weekday) %>% 
           dplyr::summarise(Total = n())
wm_by_weekday$Percent <- wm_by_weekday$Total/dim(df_wm)[1] * 100
wm_by_weekday

ggplot(wm_by_weekday, aes(Weekday, Total, fill = Weekday)) + 
      geom_bar(stat = "identity") +
      ggtitle("White Males - Crimes By Weekday ") + 
      xlab("Day of the Week") + ylab("Count") + 
      theme(legend.position = "none")
```

#### White Males - By Month
```{r}
wm_by_month <- df_wm %>% 
            group_by(Month) %>% 
            dplyr::summarise(Total = n())

wm_by_month$Percent <- wm_by_month$Total/dim(df_wm)[1] * 100
wm_by_month

ggplot(wm_by_month, aes(Month, Total, fill = Month)) + 
        geom_bar(stat = "identity") + 
        ggtitle("White Males - Crimes By Month") + 
        xlab("Month") + 
        ylab("Count") + 
        theme(legend.position = "none")

ggplot(wm_by_month, aes(x=Month, y=Total, group=1)) + geom_line()
```

####White Men - Yearly Crime Incidents
```{r}
wm_by_year = df_wm %>% group_by(Arrest_Year) %>% 
           dplyr::summarise(Total = n())
wm_by_year$Percent <- wm_by_year$Total/dim(df_wm)[1] * 100
wm_by_year

ggplot(wm_by_year, aes(Arrest_Year, Total, fill = Arrest_Year)) + 
      geom_bar(stat = "identity") +
      ggtitle("White Males - Crimes By Year ") + 
      xlab("Year") + ylab("Count") + 
      theme(legend.position = "none")

ggplot(wm_by_year, aes(x=Arrest_Year, y=Total, group=1)) + geom_line()
```


#### Let us get into crime types...

```{r}
wm_by_cat <- df_wm %>% 
          group_by(Arrest_Category) %>% 
          dplyr::summarise(Total = n()) %>% 
          arrange(desc(Total))

wm_by_cat[1:10,]

ggplot(wm_by_cat, aes(reorder(Arrest_Category, Total), Total)) + 
    geom_bar(stat = "identity") + coord_flip() +  
    scale_y_continuous(breaks = seq(0,3000,500)) + 
    ggtitle("Crimes By Arrest Category") + 
    xlab("Crime Type") + 
    ylab("Number of Incidents")
```

```{r}
wm_by_cat_year <- df_wm %>% group_by(Arrest_Year, Arrest_Category) %>% 
                dplyr::summarise(Total = n())

wm_by_cat_year[1:10,]

ggplot(wm_by_cat_year, aes(reorder(Arrest_Category, Total), Total, fill = Arrest_Year)) + 
    geom_bar(stat = "identity") + 
    scale_y_continuous(breaks = seq(0,3000,500)) + 
    coord_flip() + ggtitle("Crimes By Code and Year") + 
    xlab("Crime Text Code") + 
    ylab("Total Crimes")
```


## Some Top Crimes

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}
plotcrime  <- function(crime) {
    crimes <- df_wm[df_wm$Arrest_Category == crime,] 
    
    crimes_by_date <- crimes %>% group_by(Arrest_Date) %>% dplyr::summarise(Total = n())
    crimes_by_date$Arrest_Date <- as.Date(crimes_by_date$Arrest_Date)
    plot <- ggplot(crimes_by_date, aes(Arrest_Date, Total, color = Arrest_Date )) + geom_line() + ggtitle(paste(crime," - (Daily Count - 2016-2021)", sep = " ")) + xlab("Date") 
    
    plot
}

plotcrime("Simple Assault")
plotcrime("Traffic Violations")
plotcrime("Release Violations/Fugitive")
plotcrime("Driving/Boating While Intoxicated")
plotcrime("Theft")
plotcrime("Narcotics")
plotcrime("Liquor Law Violations")
plotcrime("Disorderly Conduct")
plotcrime("Damage to Property")
plotcrime("Prostitution")
plotcrime("Offenses Against Family & Children")
```

#### Location Stuff
```{r}
unique(df_wm$Arrest_Location_District)
table(df_wm$Arrest_Location_District)
unique(df_wm$Offense_Location_District)
table(df_wm$Offense_Location_District)

### drop the unknowns here .. they are few..
```

```{r}
wm_by_ALD <- df_wm %>% group_by(Arrest_Location_District) %>% 
         dplyr::summarise(Total = n()) %>% 
         dplyr::arrange(desc(Total))
wm_by_ALD2 = wm_by_ALD[1:7,]

wm_by_OLD <- df_wm %>% group_by(Offense_Location_District) %>% 
         dplyr::summarise(Total = n()) %>% 
         dplyr::arrange(desc(Total))
wm_by_OLD2 = wm_by_OLD[1:7,]

ggplot(wm_by_ALD2, aes(reorder(Arrest_Location_District, -Total), Total)) + 
      geom_bar(stat = "identity") + 
      ggtitle("Crimes by Arrest Location District") + 
      xlab("Location District") + 
      ylab("Total Crimes") 

ggplot(wm_by_OLD2, aes(reorder(Offense_Location_District, -Total), Total)) + 
      geom_bar(stat = "identity") + 
      ggtitle("Crimes by Offense Location District") + 
      xlab("Location District") + 
      ylab("Total Crimes") 

# top 5 crimes in each district
#ALD_dc_top7 <- wm_by_ALD$Arrest_Location_District[1:5]

#ALD_top7_dc <- subset(df_wm, Arrest_Location_District %in% wm_by_ALD$Arrest_Location_District[1:5])
#ALD_top7_dc$Arrest_Location_District <- factor(ALD_top7_dc$Arrest_Location_District)

#ggplot(ALD_top7_dc, aes(Arrest_Category, fill = Arrest_Location_District)) + 
      #geom_bar(position = "dodge") + 
      #ggtitle("Crimes by District Police HeadQuarters - Top 5") + 
      #xlab("Police HQ") + 
      #ylab("Total Crimes") 

#top crime by ARREST Location District 
ALD_by_crime <- df_wm  %>% 
      group_by(Arrest_Location_District, Arrest_Category) %>% 
      dplyr::summarise(Total = n()) %>% 
      arrange(desc(Total)) %>% top_n(n = 1)
ALD_by_crime1 = ALD_by_crime[1:7,]

#dc_by_crime <- as.data.frame(dc_by_crime)
#dc_by_crime$Dc_Dist <- factor(dc_by_crime$Dc_Dist)
#dc_by_crime$Text_General_Code <- factor(dc_by_crime$Text_General_Code)

ggplot(ALD_by_crime1, aes(Arrest_Location_District, Total, fill = Arrest_Category)) + 
      geom_bar(stat = "identity") + 
      ggtitle("Top Crime by Arrest Location District") + 
      xlab("Location District") + 
      ylab("Total") 

#top crime by OFFENSE Location District
OLD_by_crime <- df_wm  %>% 
      group_by(Offense_Location_District, Arrest_Category) %>% 
      dplyr::summarise(Total = n()) %>% 
      arrange(desc(Total)) %>% top_n(n = 1)
OLD_by_crime1 = OLD_by_crime[1:7,]

#dc_by_crime <- as.data.frame(dc_by_crime)
#dc_by_crime$Dc_Dist <- factor(dc_by_crime$Dc_Dist)
#dc_by_crime$Text_General_Code <- factor(dc_by_crime$Text_General_Code)

ggplot(OLD_by_crime1, aes(Offense_Location_District, Total, fill = Arrest_Category)) + 
      geom_bar(stat = "identity") + 
      ggtitle("Top Crime by Offense Location District") + 
      xlab("Location District") + 
      ylab("Total") 
```



