---
title: "midterm project team 5"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
date: "`r Sys.Date()`"
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(ezids)
library(dplyr)
library(readr)
library(tidyr)
library(knitr)
library(magrittr)
```


# Research Topic  
Our research topic is **Trend of Major Types of Crimes commited by White Males in the DC Area in 2016-2021**. We chose this topic because we are interested in the impact of COVID-19 on crimes. We will use [the data provided by the Metropolitan Police of DC](https://mpdc.dc.gov/node/1379551) regarding adult arrests over a time period stretching between 2016-2021.

# Data Shaping
## Read Data
We read the data .CSV files of adults arrest in DC area from 2016-2021

```{r }
df_2016<-data.frame(read.csv("Arrests 2016 Public.csv"))
df_2017<-data.frame(read.csv("Arrests 2017 Public.csv"))
df_2018<-data.frame(read.csv("Arrests by Year, 2018.csv"))
df_2019<-data.frame(read.csv("Arrests by Year, 2019.csv"))
df_2020<-data.frame(read.csv("Arrests by Year 2020.csv"))
df_2021<-data.frame(read.csv("2021 Adult Arrests.csv"))

c16 <- c(colnames(df_2016))
c18 <- c(colnames(df_2018))
```

The column names of the data in 2016 and 2017 were not the same with others. The below table shows the column names of the data in 2016 and the data in 2018.

|col #|2016       |2018       |
|:---:|:---------:|:---------:|
|  1  |`r c16[1]` |`r c18[1]` |
|  2  |`r c16[2]` |`r c18[2]` |
|  3  |`r c16[3]` |`r c18[3]` |
|  4  |`r c16[4]` |`r c18[4]` |
|  5  |`r c16[5]` |`r c18[5]` |
|  6  |`r c16[6]` |`r c18[6]` |
|  7  |`r c16[7]` |`r c18[7]` |
|  8  |`r c16[8]` |`r c18[8]` |
|  9  |`r c16[9]` |`r c18[9]` |
| 10  |`r c16[10]`|`r c18[10]`|
| 11  |`r c16[11]`|`r c18[11]`|
| 12  |`r c16[12]`|`r c18[12]`|
| 13  |`r c16[13]`|`r c18[13]`|
| 14  |`r c16[14]`|`r c18[14]`|
| 15  |`r c16[15]`|`r c18[15]`|
| 16  |`r c16[16]`|`r c18[16]`|
| 17  |`r c16[17]`|`r c18[17]`|
| 18  |`r c16[18]`|`r c18[18]`|
| 19  |`r c16[19]`|`r c18[19]`|
| 20  |`r c16[20]`|`r c18[20]`|
| 21  |`r c16[21]`|`r c18[21]`|
| 22  |`r c16[22]`|`r c18[22]`|
| 23  |`r c16[23]`|`r c18[23]`|
| 24  |`r c16[24]`|`r c18[24]`|
| 25  |`r c16[25]`|`r c18[25]`|
| 26  |`r c16[26]`|`r c18[26]`|


## Merge Multiple CSV Files and Drop Some Columns  
The column names were same from the first column to the 14th column in both data. On the other hand, the name and order of 15th and latter columns were a bit different in those data. The latter columns were about locations, and we were not very interested in the detail location. Therefore, we deleted the latter columns except for the 16th and 22nd columns. In addition, we dropped `CNN` (col #5) and `Arrest.Number.` (col #6) because they were IDs and useless for our analysis.
  
The format of date was different from years; the data in 2016 and 2017 has the format like `r df_2016$Arrest_Date[1]`, the data in 2018 to 2020 has the format like `r df_2018$Arrest_Date[1]`, and the data in 2021 has the format like `r df_2021$Arrest_Date[1]`. We coverted Since different date formats for different years are difficult to analyze, we will unify the date format to "yyyy-mm-dd".
  
After deleting some columns and changing the date format, we binded data frames by rows.


```{r}
# convert format
df_2018$Arrest.Date <- as.Date(df_2018$Arrest.Date, format = "%m/%d/%Y") %>% format()
df_2019$Arrest.Date <- as.Date(df_2019$Arrest.Date, format = "%m/%d/%Y") %>% format()
df_2020$Arrest.Date <- as.Date(df_2020$Arrest.Date, format = "%m/%d/%Y") %>% format()
df_2021$Arrest.Date <- as.Date(df_2021$Arrest.Date, format = "%Y/%m/%d") %>% format()

#bind df_2016 and df_2017, and delete some columns
df_16_17 <- rbind(df_2016, df_2017)[,-c(5,6,15,17:21,23:26)]
names(df_16_17)[c(13,14)] <- c('Arrest.Location.District','Offense.Location.District')   #rename columns

#bind df_2018 - df_2021, and delete some columns
df_18_21 <- rbind(df_2018, df_2019, df_2020, df_2021)[,-c(5,6,15,17:21,23:26)] 

DF<-rbind(df_16_17,df_18_21)
```

  
## Correct Anomalies   
### Remove abnormal values  
To see whether there were abnormal values, we created the table showing some statistics for numerical variables.

```{r}
xkablesummary(subset(DF,select=c(Arrest.Year, Arrest.Hour, Age)))
```

The maximum age was too old. `r nrow(DF[DF$Age>=100,])` rows were assigned an age of over 100 years (`r min(DF[DF$Age>=100,]$Age)`-`r max(DF[DF$Age>=100,]$Age)` ) in these data, and it seemed to be wrong. Therefore, we dropped these rows.  

```{r}
DF <- DF[!DF$Age>=100,]
```
### Some data cleaning.. Dropping, Binding and Renaming of columns as needed.
```{r}

# replace dots with underscore for clarity sake, i think..
names(DF) = gsub("[.]", "_", names(DF))
colnames(DF)

```




```{r}
#find unique values in the race, sex and arrest_category columns.
#unique(DF$Defendant_Race)
#unique(DF$Defendant_Sex)
#unique(DF$Arrest_Category)

# most likely "UNK" is the same as "Unknown", so we can change this
DF$Defendant_Race[DF$Defendant_Race == 'UNK'] <- 'UNKNOWN'
#unique(DF$Defendant_Race) - check that it changed

#same issue, "unk" is very likely "unknown", so change it.
DF$Defendant_Sex[DF$Defendant_Sex == 'UNK'] <- 'UNKNOWN'
#unique(DF$Defendant_Sex) - check that it changed

# Arrest category -  4 different types of Fraud & Financial crimes , 3 types of Release Violations/Fugitive -- group them into one.

DF$Arrest_Category = gsub("Fraud and Financial Crimes.*","Fraud and Financial Crimes", DF$Arrest_Category)

DF$Arrest_Category = gsub("Release Violations/Fugitive.*","Release Violations/Fugitive",DF$Arrest_Category)

#sort(unique(DF$Arrest_Category)) - check that new changes were made.
```

### Missing Values
```{r}
sapply(DF, function(x) sum(is.na(x)))
```
##### Our variables of concern in thsi dataset contain rich data.. over 95% of data available in each useful column.. will not delete any rows


```{r}
#get month and day variables.. might be interesting, who knows?
DF <- separate(DF, col = Arrest_Date, into = c("Year","Month","Day"), sep = "-", remove = FALSE, fill="left")
#remove the new year column formed, it is redundant.. we already have Year column
DF = DF[,-4]
colnames(DF)
```


```{r}
library(lubridate)
# Factorize some variables
DF$Arrest_Year = as.factor(DF$Arrest_Year)
DF$Month = as.factor(DF$Month)
DF$Day = as.factor(DF$Day)
DF$Defendant_Race = as.factor(DF$Defendant_Race)
DF$Defendant_Sex = as.factor(DF$Defendant_Sex)
DF$Arrest_Location_District = as.factor(DF$Arrest_Location_District)
DF$Offense_Location_District = as.factor(DF$Offense_Location_District)
# convert to date format
DF$Arrest_Date = as.Date(DF$Arrest_Date)
# Day format
DF$Day = day(DF$Arrest_Date)
# i want to create a week-day variable
DF$Weekday = weekdays(DF$Arrest_Date)
DF$Weekday = factor(DF$Weekday, levels = as.character(wday(c(2:7,1), label=TRUE, abbr=FALSE)))

# convert crime types to factors
DF$Arrest_Category = as.factor(DF$Arrest_Category)
```


### Correct inconsistent values    
`Arrest_Category` had some different values for 2021 and other years:  

* Data in 2021 had "Release Violations/Fugitive (Fug)" and "Release Violations/Fugitive (Warr)" although data in other years have "Release Violations/Fugitive" instead of them.  
* Data in 2021 had "Fraud and Financial Crimes (Frau)" although data in other years have "Fraud and Financial Crimes".  

Therefore, we coverted these values in 2021 into the correspond values in other years.  


```{r}
DF <- mutate(DF, Arrest_Category = gsub(Arrest_Category, pattern = "Release Violations/Fugitive.*", replacement = "Release Violations/Fugitive"))
DF <- mutate(DF, Arrest_Category = gsub(Arrest_Category, pattern = "Fraud and Financial Crimes.*", replacement = "Fraud and Financial Crimes"))
```

## Remove Unnecessary Rows  
Since we were interested in crimes committed by while males, we dropped rows where the value of `Defendant_Race` was not "White". The structure of the final data is shown in the below table.

```{r}
DF_WM <- subset(DF, subset = Defendant_Race=='WHITE' & Defendant_Sex=='MALE')

data.frame(column_name = names(DF_WM),
           class = sapply(DF_WM, typeof),
           first_values = sapply(DF_WM, function(x) paste0(head(x),  collapse = ", ")),
           row.names = NULL) %>% 
  kable("simple", caption = 'Data frame structure')
```

# EDA

## Crimes Committed by All 

```{r echo=FALSE, warning=FALSE, fig.width=8, fig.height=5.5}

by_date <- DF %>% group_by(Arrest_Date) %>% dplyr::summarise(Total = n())
ggplot(by_date, aes(Arrest_Date, Total, color = Arrest_Date)) + 
  geom_line() 
  #geom_vline(xintercept = "2020-03-11")

```


### Hour of the day.. at what time do these crimes occur the most?

```{r}
by_hour <- DF %>% 
           group_by(Arrest_Hour) %>% 
           dplyr::summarise(Total = n())
by_hour

ggplot(by_hour, aes(Arrest_Hour, Total, color = Arrest_Hour)) + 
    geom_line() + 
    ggtitle("Crimes By Hour") + 
    xlab("Hour of the Day") + 
    ylab("Total Crimes") 
```


### Day  .. What day of the month has the highest crime incidents?
```{r}
by_day <- DF %>% 
           group_by(Day) %>% 
           dplyr::summarise(Total = n())
by_day

ggplot(by_day, aes(Day, Total, color = Day)) + 
    geom_line() + 
    ggtitle("Crimes By Day") + 
    xlab("Day of the Month") + 
    ylab("Total Crimes")
```

### Day of the week..
```{r}
by_weekday = DF %>% group_by(Weekday) %>% 
           dplyr::summarise(Total = n())
by_weekday$Percent <- by_weekday$Total/dim(DF)[1] * 100
by_weekday

ggplot(by_weekday, aes(Weekday, Total, fill = Weekday)) + 
      geom_bar(stat = "identity") +
      ggtitle("Crimes By Weekday ") + 
      xlab("Day of the Week") + ylab("Count") + 
      theme(legend.position = "none")
```

### Monthly crime incidence
```{r}
by_month <- DF %>% 
            group_by(Month) %>% 
            dplyr::summarise(Total = n())

by_month$Percent <- by_month$Total/dim(DF)[1] * 100
by_month

#ggplot(by_month, aes(Month, Total, fill = Month)) + 
        #geom_bar(stat = "identity") + 
        #ggtitle("Crimes By Month") + 
        #xlab("Month") + 
        #ylab("Count") + 
        #theme(legend.position = "none")

ggplot(by_month, aes(x=Month, y=Total, group=1)) + geom_line()
```



### Crime incidence grouped into yearly plots..
```{r}
by_year = DF %>% group_by(Arrest_Year) %>% 
           dplyr::summarise(Total = n())
by_year$Percent <- by_year$Total/dim(DF)[1] * 100
by_year

#ggplot(by_year, aes(Arrest_Year, Total, fill = Arrest_Year)) + 
      #geom_bar(stat = "identity") +
      #ggtitle("Crimes By Year ") + 
      #xlab("Year") + ylab("Count") + 
      #theme(legend.position = "none")

ggplot(by_year, aes(x=Arrest_Year, y=Total, group=1)) + geom_line()
```


### Some Boxplots

```{r age vs year boxplot}
PADM = ggplot(DF, aes(group = factor(Arrest_Year), y = Age,x= Arrest_Year, fill = factor(Arrest_Year))) + 
  geom_boxplot() + 
  geom_boxplot(outlier.shape=8, outlier.size=5) +
  labs(title="Age VS Year", x="Year", y = "Age")
PADM

```

This plot is to compare the age of people who get arrested with each different year. From the plot, we can see that there are lots of outliers. We need to get rid of the outliers first.

```{r remove outliers}
Q1 = quantile(DF$Age, .25)
Q3 = quantile(DF$Age, .75)
IQR = IQR(DF$Age)

#only keep rows in dataframe that have values within 1.5*IQR of Q1 and Q3
ndf = subset(DF, DF$Age> (Q1 - 1.5*IQR) & DF$Age< (Q3 + 1.5*IQR))

#view row and column count of new data frame
dim(ndf) 
dim(DF)

```
Removed 834 outliers.


```{r }
ATY = ggplot(ndf, aes(group = factor(Arrest_Year), y = Age, x= Arrest_Year, fill = factor(Arrest_Year))) + 
  geom_boxplot() + 
  geom_boxplot(outlier.shape=8, outlier.size=5) +
  labs(title="Age VS Year", x="Year", y = "Age")
ATY


```
After remove the ourliers, we could clearly see that as year goes up, the minimum age goes up a little bit. The maximum age from this sample goes down. The median is pretty much same compare to different years. 

There are less younger criminals as year passing from 2016 to 2020 based on this sample. Criminal with age from 30 to 35 arrested more than other ages, which also probably means that there are more offenders with age from 30 to 35.

Why boxplot?
The advantage of consider median over sample mean is that it is less affected by extreme observations.

```{r }
unique(DF$Defendant_Race)
rrw = sum(DF$Defendant_Race == "WHITE")
rrb = sum(DF$Defendant_Race == "BLACK")
rra = sum(DF$Defendant_Race == "ASIAN")
rrw
rrb
rra
```



```{r }
unique(DF$Arrest_Category)

```



```{r }
ss = subset(DF,DF$Arrest_Category == "Sex Abuse")
HH = ggplot(ss, aes(group = factor(Arrest_Year), y = Arrest_Hour,x= Arrest_Year, fill = factor(Arrest_Year))) + 
  geom_boxplot() + 
  geom_boxplot(outlier.shape=8, outlier.size=5) +
  labs(title="Arrest_Hour VS Year", x="Year", y = "Arrest_Hour")
HH
```

From the box plot, we can see that most sex abuse happens around 10am to 13pm. The sex abuse happens all the time and it changes with different years.






```{r }
tt = subset(DF,DF$Arrest_Category == "Theft")
HHH = ggplot(tt, aes(group = factor(Arrest_Year), y = Arrest_Hour,x= Arrest_Year, fill = factor(Arrest_Year))) + 
  geom_boxplot() + 
  geom_boxplot(outlier.shape=8, outlier.size=5) +
  labs(title="Arrest_Hour VS Year", x="Year", y = "Arrest_Hour")
HHH



```

From the box plot, we can see that most theft happens around 15pm and they all super same with each year except year 2019. The theft always happening from 11am to 19 pm. That's a funny fact. 


## Crimes Committed by White Male

```{r echo=FALSE}
dff_2016<-df_2016[,1:14]
dff_2017<-df_2017[,1:14]
dff_2018<-df_2018[,1:14]
dff_2019<-df_2019[,1:14]
dff_2020<-df_2020[,1:14]
dff_2021<-df_2021[,1:14]


DFxx<-rbind(dff_2016,dff_2017,dff_2018,dff_2019,dff_2020,dff_2021)
xx<-which(DFxx$Defendant.Sex == "UNK")
xxx<-which(DFxx$Defendant.Sex == "UNKNOWN")
xxxx<-which(DFxx$Defendant.Sex == "FEMALE")
DF2<- DFxx[-c(xx,xxx,xxxx), ]


yy<-which(DF2$Defendant.Race == "BLACK")
yyy<-which(DF2$Defendant.Race == "WHITE")
DF3<- DF2[c(yy,yyy), ]
#tail(DF3)[,2:6]

DF_2016<- DF3[DF3$Arrest.Year == "2016", ]
DF_2017 <- DF3[DF3$Arrest.Year == "2017", ]
DF_2018 <- DF3[DF3$Arrest.Year == "2018", ]
DF_2019 <- DF3[DF3$Arrest.Year == "2019", ]
DF_2020 <- DF3[DF3$Arrest.Year == "2020", ]
DF_2021 <- DF3[DF3$Arrest.Year == "2021", ]
```

**Sex distribution**
```{r echo=FALSE}
 
counts <- table(DFxx$Defendant.Sex)
barplot(counts, main="Sex distribution of all years",
  xlab="Sex", col=c("darkblue","red"),
  legend = c("Sex"), beside=TRUE)
 
```
**Race distribution**
```{r}
counts <- table(DF2$Defendant.Race)
barplot(counts,las=3,names.arg = names(counts), main="Race distribution of all years among Males", col=c("red"),
  beside=TRUE)
```
From the barplot of **Sex**, we can see there is not enough female samples. From the barplot of **Race**, there are too many black people and to small other races which is not appropriate for us to do analysis. Therefore, we choose to investigate in white male crimes.

  
```{r echo=FALSE}
### Time to investigate our main focus group - White Males - EDA
#unique(DF$Defendant_Race)
#table(DF$Defendant_Sex)
df_wm = subset(DF, subset = Defendant_Race == "WHITE" & Defendant_Sex == "MALE")
#head(df_wm, 5)

# i want to create a week-day variable
df_wm$Weekday = weekdays(df_wm$Arrest_Date)
df_wm$Weekday = factor(df_wm$Weekday, levels = as.character(wday(c(2:7,1), label=TRUE, abbr=FALSE)))
```


same pattern here as above, will dig into a few other stuff too..

### White Men - By the Hour
```{r}
wm_by_hour <- df_wm %>% 
           group_by(Arrest_Hour) %>% 
           dplyr::summarise(Total = n())
#wm_by_hour

ggplot(wm_by_hour, aes(Arrest_Hour, Total, color = Arrest_Hour)) + 
    geom_line() + 
    ggtitle("White Males - Crimes By Hour") + 
    xlab("Hour of the Day") + 
    ylab("Total Crimes")
```


### White Men - What day of the month has the highest crime incidents?
```{r echo=FALSE}
wm_by_day <- df_wm %>% 
           group_by(Day) %>% 
           dplyr::summarise(Total = n())
wm_by_day

ggplot(wm_by_day, aes(Day, Total, color = Day)) + 
    geom_line() + 
    ggtitle("White Males - Crimes By Day") + 
    xlab("Day of the Month") + 
    ylab("Total Crimes")
```

### White Men - What Day of the Week has the highest crime incidents?
```{r}
wm_by_weekday = df_wm %>% group_by(Weekday) %>% 
           dplyr::summarise(Total = n())
wm_by_weekday$Percent <- wm_by_weekday$Total/dim(df_wm)[1] * 100
wm_by_weekday

ggplot(wm_by_weekday, aes(Weekday, Total, fill = Weekday)) + 
      geom_bar(stat = "identity") +
      ggtitle("White Males - Crimes By Weekday ") + 
      xlab("Day of the Week") + ylab("Count") + 
      theme(legend.position = "none")
```

### White Males - By Month
```{r}
wm_by_month <- df_wm %>% 
            group_by(Month) %>% 
            dplyr::summarise(Total = n())

wm_by_month$Percent <- wm_by_month$Total/dim(df_wm)[1] * 100
wm_by_month

ggplot(wm_by_month, aes(Month, Total, fill = Month)) + 
        geom_bar(stat = "identity") + 
        ggtitle("White Males - Crimes By Month") + 
        xlab("Month") + 
        ylab("Count") + 
        theme(legend.position = "none")

ggplot(wm_by_month, aes(x=Month, y=Total, group=1)) + geom_line()
```

### White Men - Yearly Crime Incidents
```{r}
wm_by_year = df_wm %>% group_by(Arrest_Year) %>% 
           dplyr::summarise(Total = n())
wm_by_year$Percent <- wm_by_year$Total/dim(df_wm)[1] * 100
wm_by_year

ggplot(wm_by_year, aes(Arrest_Year, Total, fill = Arrest_Year)) + 
      geom_bar(stat = "identity") +
      ggtitle("White Males - Crimes By Year ") + 
      xlab("Year") + ylab("Count") + 
      theme(legend.position = "none")

ggplot(wm_by_year, aes(x=Arrest_Year, y=Total, group=1)) + geom_line()
```


#### Let us get into crime types...

```{r}
wm_by_cat <- df_wm %>% 
          group_by(Arrest_Category) %>% 
          dplyr::summarise(Total = n()) %>% 
          arrange(desc(Total))

wm_by_cat[1:10,]

ggplot(wm_by_cat, aes(reorder(Arrest_Category, Total), Total)) + 
    geom_bar(stat = "identity") + coord_flip() +  
    scale_y_continuous(breaks = seq(0,3000,500)) + 
    ggtitle("Crimes By Arrest Category") + 
    xlab("Crime Type") + 
    ylab("Number of Incidents")
```

```{r}
wm_by_cat_year <- df_wm %>% group_by(Arrest_Year, Arrest_Category) %>% 
                dplyr::summarise(Total = n())

wm_by_cat_year[1:10,]

ggplot(wm_by_cat_year, aes(reorder(Arrest_Category, Total), Total, fill = Arrest_Year)) + 
    geom_bar(stat = "identity") + 
    scale_y_continuous(breaks = seq(0,3000,500)) + 
    coord_flip() + ggtitle("Crimes By Code and Year") + 
    xlab("Crime Text Code") + 
    ylab("Total Crimes")
```


### Some Top Crimes

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}
plotcrime  <- function(crime) {
    crimes <- df_wm[df_wm$Arrest_Category == crime,] 
    
    crimes_by_date <- crimes %>% group_by(Arrest_Date) %>% dplyr::summarise(Total = n())
    crimes_by_date$Arrest_Date <- as.Date(crimes_by_date$Arrest_Date)
    plot <- ggplot(crimes_by_date, aes(Arrest_Date, Total, color = Arrest_Date )) + geom_line() + ggtitle(paste(crime," - (Daily Count - 2016-2021)", sep = " ")) + xlab("Date") 
    
    plot
}

plotcrime("Simple Assault")
plotcrime("Traffic Violations")
plotcrime("Release Violations/Fugitive")
plotcrime("Driving/Boating While Intoxicated")
plotcrime("Theft")
plotcrime("Narcotics")
plotcrime("Liquor Law Violations")
plotcrime("Disorderly Conduct")
plotcrime("Damage to Property")
plotcrime("Prostitution")
plotcrime("Offenses Against Family & Children")
```
We see there are some wired high peaks in the count plots above. This is due to some protests in DC area which caused the surge of crimes. If we remove these peaks, they will be simliar to other plots, but we cannot, these are related to the events happened in the real world.

#### Location Stuff
```{r}
unique(df_wm$Arrest_Location_District)
table(df_wm$Arrest_Location_District)
unique(df_wm$Offense_Location_District)
table(df_wm$Offense_Location_District)

### drop the unknowns here .. they are few..
```

```{r}
wm_by_ALD <- df_wm %>% group_by(Arrest_Location_District) %>% 
         dplyr::summarise(Total = n()) %>% 
         dplyr::arrange(desc(Total))
wm_by_ALD2 = wm_by_ALD[1:7,]

wm_by_OLD <- df_wm %>% group_by(Offense_Location_District) %>% 
         dplyr::summarise(Total = n()) %>% 
         dplyr::arrange(desc(Total))
wm_by_OLD2 = wm_by_OLD[1:7,]

ggplot(wm_by_ALD2, aes(reorder(Arrest_Location_District, -Total), Total)) + 
      geom_bar(stat = "identity") + 
      ggtitle("Crimes by Arrest Location District") + 
      xlab("Location District") + 
      ylab("Total Crimes") 

ggplot(wm_by_OLD2, aes(reorder(Offense_Location_District, -Total), Total)) + 
      geom_bar(stat = "identity") + 
      ggtitle("Crimes by Offense Location District") + 
      xlab("Location District") + 
      ylab("Total Crimes") 

# top 5 crimes in each district
#ALD_dc_top7 <- wm_by_ALD$Arrest_Location_District[1:5]

#ALD_top7_dc <- subset(df_wm, Arrest_Location_District %in% wm_by_ALD$Arrest_Location_District[1:5])
#ALD_top7_dc$Arrest_Location_District <- factor(ALD_top7_dc$Arrest_Location_District)

#ggplot(ALD_top7_dc, aes(Arrest_Category, fill = Arrest_Location_District)) + 
      #geom_bar(position = "dodge") + 
      #ggtitle("Crimes by District Police HeadQuarters - Top 5") + 
      #xlab("Police HQ") + 
      #ylab("Total Crimes") 

#top crime by ARREST Location District 
ALD_by_crime <- df_wm  %>% 
      group_by(Arrest_Location_District, Arrest_Category) %>% 
      dplyr::summarise(Total = n()) %>% 
      arrange(desc(Total)) %>% top_n(n = 1)
ALD_by_crime1 = ALD_by_crime[1:7,]

#dc_by_crime <- as.data.frame(dc_by_crime)
#dc_by_crime$Dc_Dist <- factor(dc_by_crime$Dc_Dist)
#dc_by_crime$Text_General_Code <- factor(dc_by_crime$Text_General_Code)

ggplot(ALD_by_crime1, aes(Arrest_Location_District, Total, fill = Arrest_Category)) + 
      geom_bar(stat = "identity") + 
      ggtitle("Top Crime by Arrest Location District") + 
      xlab("Location District") + 
      ylab("Total") 

#top crime by OFFENSE Location District
OLD_by_crime <- df_wm  %>% 
      group_by(Offense_Location_District, Arrest_Category) %>% 
      dplyr::summarise(Total = n()) %>% 
      arrange(desc(Total)) %>% top_n(n = 1)
OLD_by_crime1 = OLD_by_crime[1:7,]

#dc_by_crime <- as.data.frame(dc_by_crime)
#dc_by_crime$Dc_Dist <- factor(dc_by_crime$Dc_Dist)
#dc_by_crime$Text_General_Code <- factor(dc_by_crime$Text_General_Code)

ggplot(OLD_by_crime1, aes(Offense_Location_District, Total, fill = Arrest_Category)) + 
      geom_bar(stat = "identity") + 
      ggtitle("Top Crime by Offense Location District") + 
      xlab("Location District") + 
      ylab("Total") 
```

### Number of Each Crime


We created some bar plots to see the number of occurrences per type of crime.  
The Bar plots of crimes in each year are as follows:

```{r, fig.show="hold", out.width="48%"}

ggplot(subset(DF_WM,Arrest_Year == 2016), aes(forcats::fct_infreq(Arrest_Category))) +
  ggtitle("Figure 4: Bar plot of crimes in 2016") + xlab("crime types") + geom_bar() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

ggplot(subset(DF_WM,Arrest_Year == 2017), aes(forcats::fct_infreq(Arrest_Category))) +
  ggtitle("Figure 5: Bar plot of crimes in 2017") + xlab("crime types") + geom_bar() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

ggplot(subset(DF_WM,Arrest_Year == 2018), aes(forcats::fct_infreq(Arrest_Category))) +
  ggtitle("Figure 6: Bar plot of crimes in 2018") + xlab("crime types") + geom_bar() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

ggplot(subset(DF_WM,Arrest_Year == 2019), aes(forcats::fct_infreq(Arrest_Category))) +
  ggtitle("Figure 7: Bar plot of crimes in 2019") + xlab("crime types") + geom_bar() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

ggplot(subset(DF_WM,Arrest_Year == 2020), aes(forcats::fct_infreq(Arrest_Category))) +
  ggtitle("Figure 8: Bar plot of crimes in 2020") + xlab("crime types") + geom_bar() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

ggplot(subset(DF_WM,Arrest_Year == 2021), aes(forcats::fct_infreq(Arrest_Category))) +
  ggtitle("Figure 9: Bar plot of crimes in 2021") + xlab("crime types") + geom_bar() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

```

"Offenses Against Family & Children" have been increasing after COVD-19.

```{r}
cnt_2016 <- table(subset(DF_WM,Arrest_Year==2016)$Arrest_Category)
pos_2016 <- order(cnt_2016, decreasing = TRUE)[1:6]
crime_2016 <- names(cnt_2016)[pos_2016]

cnt_2017 <- table(subset(DF_WM,Arrest_Year==2017)$Arrest_Category)
pos_2017 <- order(cnt_2017, decreasing = TRUE)[1:7]
crime_2017 <- names(cnt_2017)[pos_2017]

cnt_2018 <- table(subset(DF_WM,Arrest_Year==2018)$Arrest_Category)
pos_2018 <- order(cnt_2018, decreasing = TRUE)[1:6]
crime_2018 <- names(cnt_2018)[pos_2018]

cnt_2019 <- table(subset(DF_WM,Arrest_Year==2019)$Arrest_Category)
pos_2019 <- order(cnt_2019, decreasing = TRUE)[1:7]
crime_2019 <- names(cnt_2019)[pos_2019]

cnt_2020 <- table(subset(DF_WM,Arrest_Year==2020)$Arrest_Category)
pos_2020 <- order(cnt_2020, decreasing = TRUE)[1:7]
crime_2020 <- names(cnt_2020)[pos_2020]

cnt_2021 <- table(subset(DF_WM,Arrest_Year==2021)$Arrest_Category)
pos_2021 <- order(cnt_2021, decreasing = TRUE)[1:7]
crime_2021 <- names(cnt_2021)[pos_2021]
```
The top 6 crimes (or 7 crimes when 'Other Crimes' are included) in each year are as follows.  

| Rank | 2016 | 2017 | 2018 | 2019 | 2020 | 2021 |
|:-:|:-:|:-:|:-:|:-:|:-:|:-:|
|1|`r crime_2016[1]`|`r crime_2017[1]`|`r crime_2018[1]`|`r crime_2019[1]`|`r crime_2020[1]`|`r crime_2021[1]`|
|2|`r crime_2016[2]`|`r crime_2017[2]`|`r crime_2018[2]`|`r crime_2019[2]`|`r crime_2020[2]`|`r crime_2021[2]`|
|3|`r crime_2016[3]`|`r crime_2017[3]`|`r crime_2018[3]`|`r crime_2019[3]`|`r crime_2020[3]`|`r crime_2021[3]`|
|4|`r crime_2016[4]`|`r crime_2017[4]`|`r crime_2018[4]`|`r crime_2019[4]`|`r crime_2020[4]`|`r crime_2021[4]`|
|5|`r crime_2016[5]`|`r crime_2017[5]`|`r crime_2018[5]`|`r crime_2019[5]`|`r crime_2020[5]`|`r crime_2021[5]`|
|6|`r crime_2016[6]`|`r crime_2017[6]`|`r crime_2018[6]`|`r crime_2019[6]`|`r crime_2020[6]`|`r crime_2021[6]`|
|7|`r crime_2016[7]`|`r crime_2017[7]`|`r crime_2018[7]`|`r crime_2019[7]`|`r crime_2020[7]`|`r crime_2021[7]`|


### Time Series Change in the Number of Major Crimes
To see the trend of the above major crimes, we created a line plot as follows.

```{r}
SA_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Simple Assault',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Simple Assault',]$Arrest_Year==x)})
TV_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Traffic Violations',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Traffic Violations',]$Arrest_Year==x)})
RV_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Release Violations/Fugitive',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Release Violations/Fugitive',]$Arrest_Year==x)})
DI_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Driving/Boating While Intoxicated',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Driving/Boating While Intoxicated',]$Arrest_Year==x)})
N_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Narcotics',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Narcotics',]$Arrest_Year==x)})
LV_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Liquor Law Violations',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Liquor Law Violations',]$Arrest_Year==x)})
T_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Theft',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Theft',]$Arrest_Year==x)})
DV_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Offenses Against Family & Children',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Offenses Against Family & Children',]$Arrest_Year==x)})
DC_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Disorderly Conduct',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Disorderly Conduct',]$Arrest_Year==x)})
P_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Prostitution',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Prostitution',]$Arrest_Year==x)})
DP_cnt <- sapply(unique(DF_WM[DF_WM$Arrest_Category=='Damage to Property',]$Arrest_Year),
                       function(x){sum(DF_WM[DF_WM$Arrest_Category=='Damage to Property',]$Arrest_Year==x)})
year_lst <- 2016:2021

major_crimes_df <- data.frame(year_lst, SA_cnt, TV_cnt, RV_cnt, DI_cnt, N_cnt, LV_cnt, T_cnt, DV_cnt, DC_cnt, P_cnt, DP_cnt)

colnames(major_crimes_df) <- c('Year', 'Simple Assault', 'Traffic Violations', 'Release Violations/Fugitive', 'Driving/Boating While Intoxicated',
                               'Narcotics', 'Liquor Law Violations', 'Theft', 'Offenses Against Family & Children', 'Disorderly Conduct', 'Prostitution', 'Damage to Property')

major_crimes_df2 <- major_crimes_df %>% gather(key = 'Crimes', value = "Count", -Year)

ggplot(data=major_crimes_df2, aes(x=Year, y=Count, color=Crimes)) +
  geom_line() + geom_point()

```
  
  
**"Simple Assault"**, **"Traffic Violations"**, and **"Theft"** have clearly declined since 2020. On the other, **"Offenses Against Family & Children"** has increased in 2020 and 2021 compared to previous years. COVID-19 seems to be related to these trend change. We posed the following SMART QUESTION, and we will analyze these four crimes in detail in the following.  
  
**Is there a significant difference in "Simple Assault", "Traffic Violations", "Theft", and "Offenses Against Family & Children" trends among adult white males within the DC area between 2016 and 2021, and could COVID protocols play a role in these trend shifts?**

### Common Crimes trend among people with different generations 
group white males by age:

**Young**: 18-29; **Middle age**: 30-50; **Old**: >50.
Crimes:**"Simple Assault","Release Violations/Fugitive","Traffic Violations", "Narcotics", "Theft", "Other Crimes"**






```{r echo=FALSE}
#"Simple Assault" 18-29
SIM_young<-list()
SIM_mid<-list()
SIM_old<-list()

#YOUNG
SIM_young<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='29'][DF_2016$Age>='18']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_young,.)

SIM_young<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='29'][DF_2017$Age>='18']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_young,.)

SIM_young<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='29'][DF_2018$Age>='18']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_young,.)

SIM_young<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='29'][DF_2019$Age>='18']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_young,.)

SIM_young<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='29'][DF_2020$Age>='18']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_young,.)

SIM_young<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='29'][DF_2021$Age>='18']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_young,.)

SIM_young<-c(SIM_young[[1]],SIM_young[[2]],SIM_young[[3]],SIM_young[[4]],SIM_young[[5]],SIM_young[[6]])

#MID
SIM_mid<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='50'][DF_2016$Age>='30']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_mid,.)

SIM_mid<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='50'][DF_2017$Age>='30']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_mid,.)

SIM_mid<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='50'][DF_2018$Age>='30']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_mid,.)

SIM_mid<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='50'][DF_2019$Age>='30']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_mid,.)

SIM_mid<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='50'][DF_2020$Age>='30']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_mid,.)

SIM_mid<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='50'][DF_2021$Age>='30']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_mid,.)

SIM_mid<-c(SIM_mid[[1]],SIM_mid[[2]],SIM_mid[[3]],SIM_mid[[4]],SIM_mid[[5]],SIM_mid[[6]])

#OLD

SIM_old<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age>="51"]=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_old,.)

SIM_old<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age>='51']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_old,.)

SIM_old<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age>='51']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_old,.)

SIM_old<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age>='51']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_old,.)

SIM_old<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age>='51']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_old,.)

SIM_old<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age>='51']=="Simple Assault")["TRUE"]%>%sum()%>%append(SIM_old,.)

SIM_old<-c(SIM_old[[1]],SIM_old[[2]],SIM_old[[3]],SIM_old[[4]],SIM_old[[5]],SIM_old[[6]])


```

Release Violations/Fugitive

```{r}

#Release Violations/Fugitive
RVF_young<-list()
RVF_mid<-list()
RVF_old<-list()

#YOUNG
RVF_young<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='29'][DF_2016$Age>='18']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_young,.)

RVF_young<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='29'][DF_2017$Age>='18']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_young,.)

RVF_young<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='29'][DF_2018$Age>='18']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_young,.)

RVF_young<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='29'][DF_2019$Age>='18']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_young,.)

RVF_young<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='29'][DF_2020$Age>='18']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_young,.)

RVF_young<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='29'][DF_2021$Age>='18']=="Release Violations/Fugitive (Warr)")["TRUE"]%>%sum()%>%append(RVF_young,.)

RVF_young<-c(RVF_young[[1]],RVF_young[[2]],RVF_young[[3]],RVF_young[[4]],RVF_young[[5]],RVF_young[[6]])

#MID
RVF_mid<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='50'][DF_2016$Age>='30']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_mid,.)

RVF_mid<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='50'][DF_2017$Age>='30']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_mid,.)

RVF_mid<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='50'][DF_2018$Age>='30']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_mid,.)

RVF_mid<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='50'][DF_2019$Age>='30']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_mid,.)

RVF_mid<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='50'][DF_2020$Age>='30']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_mid,.)

RVF_mid<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='50'][DF_2021$Age>='30']=="Release Violations/Fugitive (Warr)")["TRUE"]%>%sum()%>%append(RVF_mid,.)

RVF_mid<-c(RVF_mid[[1]],RVF_mid[[2]],RVF_mid[[3]],RVF_mid[[4]],RVF_mid[[5]],RVF_mid[[6]])

#OLD

RVF_old<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age>="51"]=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_old,.)

RVF_old<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age>='51']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_old,.)

RVF_old<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age>='51']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_old,.)

RVF_old<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age>='51']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_old,.)

RVF_old<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age>='51']=="Release Violations/Fugitive")["TRUE"]%>%sum()%>%append(RVF_old,.)

RVF_old<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age>='51']=="Release Violations/Fugitive (Warr)")["TRUE"]%>%sum()%>%append(RVF_old,.)

RVF_old<-c(RVF_old[[1]],RVF_old[[2]],RVF_old[[3]],RVF_old[[4]],RVF_old[[5]],RVF_old[[6]])

```

Traffic Violations

```{r}

TRA_young<-list()
TRA_mid<-list()
TRA_old<-list()

#YOUNG
TRA_young<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='29'][DF_2016$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_young,.)

TRA_young<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='29'][DF_2017$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_young,.)

TRA_young<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='29'][DF_2018$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_young,.)

TRA_young<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='29'][DF_2019$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_young,.)

TRA_young<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='29'][DF_2020$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_young,.)

TRA_young<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='29'][DF_2021$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_young,.)

TRA_young<-c(TRA_young[[1]],TRA_young[[2]],TRA_young[[3]],TRA_young[[4]],TRA_young[[5]],TRA_young[[6]])

#MID
TRA_mid<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='50'][DF_2016$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_mid,.)

TRA_mid<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='50'][DF_2017$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_mid,.)

TRA_mid<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='50'][DF_2018$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_mid,.)

TRA_mid<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='50'][DF_2019$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_mid,.)

TRA_mid<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='50'][DF_2020$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_mid,.)

TRA_mid<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='50'][DF_2021$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_mid,.)

TRA_mid<-c(TRA_mid[[1]],TRA_mid[[2]],TRA_mid[[3]],TRA_mid[[4]],TRA_mid[[5]],TRA_mid[[6]])

#OLD

TRA_old<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age>="51"]=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_old,.)

TRA_old<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_old,.)

TRA_old<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_old,.)

TRA_old<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_old,.)

TRA_old<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_old,.)

TRA_old<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(TRA_old,.)

TRA_old<-c(TRA_old[[1]],TRA_old[[2]],TRA_old[[3]],TRA_old[[4]],TRA_old[[5]],TRA_old[[6]])

```

Narcotics
```{r}
NAR_young<-list()
NAR_mid<-list()
NAR_old<-list()

#YOUNG
NAR_young<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='29'][DF_2016$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_young,.)

NAR_young<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='29'][DF_2017$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_young,.)

NAR_young<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='29'][DF_2018$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_young,.)

NAR_young<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='29'][DF_2019$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_young,.)

NAR_young<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='29'][DF_2020$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_young,.)

NAR_young<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='29'][DF_2021$Age>='18']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_young,.)

NAR_young<-c(NAR_young[[1]],NAR_young[[2]],NAR_young[[3]],NAR_young[[4]],NAR_young[[5]],NAR_young[[6]])

#MID
NAR_mid<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='50'][DF_2016$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_mid,.)

NAR_mid<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='50'][DF_2017$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_mid,.)

NAR_mid<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='50'][DF_2018$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_mid,.)

NAR_mid<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='50'][DF_2019$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_mid,.)

NAR_mid<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='50'][DF_2020$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_mid,.)

NAR_mid<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='50'][DF_2021$Age>='30']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_mid,.)

NAR_mid<-c(NAR_mid[[1]],NAR_mid[[2]],NAR_mid[[3]],NAR_mid[[4]],NAR_mid[[5]],NAR_mid[[6]])

#OLD

NAR_old<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age>="51"]=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_old,.)

NAR_old<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_old,.)

NAR_old<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_old,.)

NAR_old<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_old,.)

NAR_old<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_old,.)

NAR_old<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age>='51']=="Traffic Violations")["TRUE"]%>%sum()%>%append(NAR_old,.)

NAR_old<-c(NAR_old[[1]],NAR_old[[2]],NAR_old[[3]],NAR_old[[4]],NAR_old[[5]],NAR_old[[6]])

```

THEFT
```{r}
#THEFT
THEFT_young<-list()
THEFT_mid<-list()
THEFT_old<-list()

#YOUNG
THEFT_young<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='29'][DF_2016$Age>='18']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_young,.)

THEFT_young<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='29'][DF_2017$Age>='18']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_young,.)

THEFT_young<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='29'][DF_2018$Age>='18']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_young,.)

THEFT_young<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='29'][DF_2019$Age>='18']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_young,.)

THEFT_young<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='29'][DF_2020$Age>='18']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_young,.)

THEFT_young<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='29'][DF_2021$Age>='18']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_young,.)

THEFT_young<-c(THEFT_young[[1]],THEFT_young[[2]],THEFT_young[[3]],THEFT_young[[4]],THEFT_young[[5]],THEFT_young[[6]])

#MID
THEFT_mid<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='50'][DF_2016$Age>='30']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_mid,.)

THEFT_mid<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='50'][DF_2017$Age>='30']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_mid,.)

THEFT_mid<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='50'][DF_2018$Age>='30']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_mid,.)

THEFT_mid<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='50'][DF_2019$Age>='30']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_mid,.)

THEFT_mid<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='50'][DF_2020$Age>='30']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_mid,.)

THEFT_mid<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='50'][DF_2021$Age>='30']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_mid,.)

THEFT_mid<-c(THEFT_mid[[1]],THEFT_mid[[2]],THEFT_mid[[3]],THEFT_mid[[4]],THEFT_mid[[5]],THEFT_mid[[6]])

#OLD

THEFT_old<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age>="51"]=="Theft")["TRUE"]%>%sum()%>%append(THEFT_old,.)

THEFT_old<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age>='51']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_old,.)

THEFT_old<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age>='51']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_old,.)

THEFT_old<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age>='51']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_old,.)

THEFT_old<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age>='51']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_old,.)

THEFT_old<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age>='51']=="Theft")["TRUE"]%>%sum()%>%append(THEFT_old,.)

THEFT_old<-c(THEFT_old[[1]],THEFT_old[[2]],THEFT_old[[3]],THEFT_old[[4]],THEFT_old[[5]],THEFT_old[[6]])

```

Other Crimes
```{r}
#Other Crimes
OTH_young<-list()
OTH_mid<-list()
OTH_old<-list()

#YOUNG
OTH_young<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='29'][DF_2016$Age>='18']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_young,.)

OTH_young<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='29'][DF_2017$Age>='18']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_young,.)

OTH_young<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='29'][DF_2018$Age>='18']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_young,.)

OTH_young<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='29'][DF_2019$Age>='18']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_young,.)

OTH_young<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='29'][DF_2020$Age>='18']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_young,.)

OTH_young<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='29'][DF_2021$Age>='18']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_young,.)

OTH_young<-c(OTH_young[[1]],OTH_young[[2]],OTH_young[[3]],OTH_young[[4]],OTH_young[[5]],OTH_young[[6]])

#MID
OTH_mid<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age<='50'][DF_2016$Age>='30']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_mid,.)

OTH_mid<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age<='50'][DF_2017$Age>='30']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_mid,.)

OTH_mid<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age<='50'][DF_2018$Age>='30']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_mid,.)

OTH_mid<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age<='50'][DF_2019$Age>='30']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_mid,.)

OTH_mid<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age<='50'][DF_2020$Age>='30']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_mid,.)

OTH_mid<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age<='50'][DF_2021$Age>='30']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_mid,.)

OTH_mid<-c(OTH_mid[[1]],OTH_mid[[2]],OTH_mid[[3]],OTH_mid[[4]],OTH_mid[[5]],OTH_mid[[6]])

#OLD

OTH_old<-table(DF_2016$Arrest.Category[DF_2016$Defendant.Race=="WHITE"][DF_2016$Age>="51"]=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_old,.)

OTH_old<-table(DF_2017$Arrest.Category[DF_2017$Defendant.Race=="WHITE"][DF_2017$Age>='51']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_old,.)

OTH_old<-table(DF_2018$Arrest.Category[DF_2018$Defendant.Race=="WHITE"][DF_2018$Age>='51']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_old,.)

OTH_old<-table(DF_2019$Arrest.Category[DF_2019$Defendant.Race=="WHITE"][DF_2019$Age>='51']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_old,.)

OTH_old<-table(DF_2020$Arrest.Category[DF_2020$Defendant.Race=="WHITE"][DF_2020$Age>='51']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_old,.)

OTH_old<-table(DF_2021$Arrest.Category[DF_2021$Defendant.Race=="WHITE"][DF_2021$Age>='51']=="Other Crimes")["TRUE"]%>%sum()%>%append(OTH_old,.)

OTH_old<-c(OTH_old[[1]],OTH_old[[2]],OTH_old[[3]],OTH_old[[4]],OTH_old[[5]],OTH_old[[6]])


```

```{r echo=FALSE}
#dataframe of 3 age stages
x_year<-c(seq(2016, 2021, by=1))
DF_white_age<-data.frame(x_year,SIM_young,SIM_mid,SIM_old,RVF_young,RVF_mid,RVF_old,TRA_young,TRA_mid,TRA_old,NAR_young,NAR_mid,NAR_old,THEFT_young,THEFT_mid,THEFT_old,OTH_young,OTH_mid,OTH_old)
head_DF_age<-head(DF_white_age)
 
```

```{r echo=FALSE}
DF_white_young<-data.frame(year=x_year,"Simple Assault"=SIM_young,"Release Violations/Fugitive"=RVF_young,"Traffic Violations"=TRA_young,"Narcotics"=NAR_young,"Theft"=THEFT_young,"Other Crimes"=OTH_young)
DF_white_mid<-data.frame(year=x_year,"Simple Assault"=SIM_mid,"Release Violations/Fugitive"=RVF_mid,"Traffic Violations"=TRA_mid,"Narcotics"=NAR_mid,"Theft"=THEFT_mid,"Other Crimes"=OTH_mid)
DF_white_old<-data.frame(year=x_year,"Simple Assault"=SIM_old,"Release Violations/Fugitive"=RVF_old,"Traffic Violations"=TRA_old,"Narcotics"=NAR_old,"Theft"=THEFT_old,"Other Crimes"=OTH_old)
head(DF_white_young)
DF_white_young<-transform(DF_white_young,age="young")
DF_white_mid<-transform(DF_white_mid,age="mid")
DF_white_old<-transform(DF_white_old,age="old")
DF_white_age2<-rbind(DF_white_young,DF_white_mid,DF_white_old)
#tail(DF_white_age2)
```



Some plots of crime trend of **different generation**
```{r echo=FALSE}

#color_ls<-list("darkorange","darkorange1","darkorange2","darkorange3","darkorange4","darkolivegreen4")
plot_young<-ggplot()+geom_line(data = DF_white_age,aes(x = x_year,y = SIM_young,colour = "Simple Assault"),size=1)+
  geom_point(data =  DF_white_age,aes(x = x_year,y = SIM_young,colour = "Simple Assault"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = RVF_young,colour ="Release Violations/Fugitive"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = RVF_young,colour = "Release Violations/Fugitive"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = TRA_young,colour ="Traffic Violations"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = TRA_young,colour = "Traffic Violations"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = NAR_young,colour ="Narcotics"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = NAR_young,colour = "Narcotics"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = THEFT_young,colour ="Theft"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = THEFT_young,colour = "Theft"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y =OTH_young,colour ="Other Crimes"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = OTH_young,colour = "Other Crimes"),size=3)+
  
  scale_colour_manual("",values = c("red","orange","yellow","green","blue","purple"))+
  xlab("Year")+ylab("CRIME COUNTS")+ ggtitle("Young (18-29)")+
  
  
 theme(panel.grid.major = element_line(color = "gray10", size = .5),
        panel.grid.minor = element_line(color = "gray70", size = .25))

plot_mid<-ggplot()+geom_line(data = DF_white_age,aes(x = x_year,y = SIM_mid,colour = "Simple Assault"),size=1)+
  geom_point(data =  DF_white_age,aes(x = x_year,y = SIM_mid,colour = "Simple Assault"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = RVF_mid,colour ="Release Violations/Fugitive"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = RVF_mid,colour = "Release Violations/Fugitive"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = TRA_mid,colour ="Traffic Violations"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = TRA_mid,colour = "Traffic Violations"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = NAR_mid,colour ="Narcotics"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = NAR_mid,colour = "Narcotics"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = THEFT_mid,colour ="Theft"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = THEFT_mid,colour = "Theft"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y =OTH_mid,colour ="Other Crimes"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = OTH_mid,colour = "Other Crimes"),size=3)+
  
  scale_colour_manual("",values = c("red","orange","yellow","green","blue","purple"))+
  xlab("Year")+ylab("CRIME COUNTS")+ ggtitle("Middle age (30-50)")+
  
  
 theme(panel.grid.major = element_line(color = "gray10", size = .5),
        panel.grid.minor = element_line(color = "gray70", size = .25))


plot_old<-ggplot()+geom_line(data = DF_white_age,aes(x = x_year,y = SIM_old,colour = "Simple Assault"),size=1)+
  geom_point(data =  DF_white_age,aes(x = x_year,y = SIM_old,colour = "Simple Assault"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = RVF_old,colour ="Release Violations/Fugitive"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = RVF_old,colour = "Release Violations/Fugitive"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = TRA_old,colour ="Traffic Violations"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = TRA_old,colour = "Traffic Violations"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = NAR_old,colour ="Narcotics"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = NAR_old,colour = "Narcotics"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y = THEFT_old,colour ="Theft"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = THEFT_old,colour = "Theft"),size=3)+
  
  geom_line(data =  DF_white_age,aes(x = x_year,y =OTH_old,colour ="Other Crimes"),size=1) + 
  geom_point(data =  DF_white_age,aes(x = x_year,y = OTH_old,colour = "Other Crimes"),size=3)+
  
  scale_colour_manual("",values = c("red","orange","yellow","green","blue","purple"))+
  xlab("Year")+ylab("CRIME COUNTS")+ ggtitle("Old age (>50)")+
  
 
 theme(panel.grid.major = element_line(color = "gray10", size = .5),
        panel.grid.minor = element_line(color = "gray70", size = .25))
```

```{r}
plot_young
plot_mid
plot_old
```

```{r echo=FALSE}
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
grid.arrange(
arrangeGrob(plot_young, plot_mid, plot_old, ncol=1, nrow=3), 
  top = "Crime trend among differenge ages",
  bottom = textGrob(
    "2016-2021 in DC",
    gp = gpar(fontface = 3, fontsize = 9),
    hjust = 1,
    x = 1
  )
)
```


**Barplot** of crime trend of white males of different generations

Plot each crime separately:

```{r}
ggplot(DF_white_age2, aes(fill=age, y=Simple.Assault, x=year)) + 
    geom_bar(position="stack", stat="identity") 

ggplot(DF_white_age2, aes(fill=age, y=Release.Violations.Fugitive, x=year)) + 
    geom_bar(position="stack", stat="identity") 

ggplot(DF_white_age2, aes(fill=age, y=Traffic.Violations
, x=year)) + 
    geom_bar(position="stack", stat="identity") 


ggplot(DF_white_age2, aes(fill=age, y=Narcotics, x=year)) + 
    geom_bar(position="stack", stat="identity") 


ggplot(DF_white_age2, aes(fill=age, y=Theft, x=year)) + 
    geom_bar(position="stack", stat="identity") 


ggplot(DF_white_age2, aes(fill=age, y=Other.Crimes
, x=year)) + 
    geom_bar(position="stack", stat="identity") 
```
Plot all 6 crimes together but with different age groups

```{r}
bar_young<-barplot(as.matrix(DF_white_young[,2:7]),
        main="Young white males \n 2016-2021",
         
        # setting y label only
        # because x-label will be our
        # barplots name
        ylab="Count",
         las=0, cex.names=0.55,
        # to plot the bars vertically
        beside=TRUE,
)
bar_mid<-barplot(as.matrix(DF_white_mid[,2:7]),
        main="Middle age white males \n 2016-2021",
         
        # setting y label only
        # because x-label will be our
        # barplots name
        ylab="Count",
         las=0, cex.names=0.55,
        # to plot the bars vertically
        beside=TRUE,
)
bar_old<-barplot(as.matrix(DF_white_old[,2:7]),
        main="Old white males \n 2016-2021",
         
        # setting y label only
        # because x-label will be our
        # barplots name
        ylab="Count",
         las=0, cex.names=0.55,
        # to plot the bars vertically
        beside=TRUE,
)


```
Though the samples of three generations (young middle age, old people) are different, the behaviors of each crime trend plots are all the same. There is no obvious difference among three groups, thus we can see **"Age"** do not have a significant effect on the trend of these common crimes.


# Analysis

Since crime is likely to be a rare event, the number of occurrences per day of a given crime is expected to follow Poisson distribution. Poisson distribution is a distribution used to describe the distribution of the number of rare phenomena when a large number of them are observed. If a distribution follows Poisson distribution, and the average number of occurrences of the phenomenon is $\lambda$, the probability that the phenomenon will occur $x$ times is given by
$$p(x) = \exp(-\lambda)\frac{\lambda^{x}}{x!}.$$
In the following, we will estimate $\lambda$ of each crime before and after COVID-19 to see there is a difference in crime trend.

## Offenses Against Family & Children
### Before COVID-19
The trend of "Offenses Against Family & Children," Domestic Violence (DV), appears to have changed after COVID-19. The frequency table of DV before COVID-19 is as follows.

```{r}
DF_WM_16_19 <- DF_WM[DF_WM$Arrest_Year%in%c(2016,2017,2018,2019),]
DF_WM_16_19_DV <- DF_WM_16_19[DF_WM_16_19$Arrest_Category=='Offenses Against Family & Children',]

# table of date and the number of occurrences
DV_day_16_19 <- sapply(unique(DF_WM_16_19_DV$Arrest_Date),
                       function(x){sum(DF_WM_16_19_DV$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*4+1 - length(DV_day_16_19)`|`r (365*4+1 - length(DV_day_16_19))/(365*4+1)`|
|1|`r length(DV_day_16_19[DV_day_16_19==1])`|`r length(DV_day_16_19[DV_day_16_19==1])/(365*4+1)`|
|2|`r length(DV_day_16_19[DV_day_16_19==2])`|`r length(DV_day_16_19[DV_day_16_19==2])/(365*4+1)`|
|3|0|0|

We can calculate $\lambda$ from the above table and $\lambda = 0.0678$. We will plot the histogram and Poisson distribution with $\lambda = 0.0678$ to check if they match or not.

```{r, fig.show="hold", out.width="48%"}

x_DV <- 0:5
y_DV <- c(1364,95,2,0,0,0)
fx <- dpois(x=x_DV, lambda=99/(365*4+1))
data_DV <- data.frame(x_DV, y_DV, fx)

ggplot(data_DV, aes(x=x_DV,y=y_DV)) +
  ggtitle("Figure 13: Histogram of DV in 2016 - 2019") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_DV) +
  ggtitle("Figure 14: Relative frequency histogram of DV in 2016 - 2019 \n and Poisson distribution with lambda = 0.0678") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_DV,y=y_DV/(365*4+1)), stat = "identity") +
  geom_line(aes(x=x_DV,y=fx), color='red') +
  geom_point(aes(x=x_DV,y=fx), color='red')

```

We can see that the Poisson distribution fits well with the histogram.   
  
Next, we try to estimate $99\%$ Confidence Interval of $\lambda$. The variance of Poisson distribution is equal to its mean ($\lambda$). Therefore, $99\%$ Confidence Interval of $\lambda$ can be written as
$$ \bar{x} - z_{*}\cdot\sqrt{\frac{\bar{x}}{n}} \leq \lambda \leq \bar{x} + z_{*}\cdot\sqrt{\frac{\bar{x}}{n}}, $$
where $\bar{x}$ is the sample mean, $n$ is the sample size, and $z_*$ is z-value corresponding to the $99\%$ confidence interval, and the value is 2.58. From this expression, **99% Confidence Interval of $\lambda$ for DV before COVID-19 is [`r round(99/(365*4+1) - 2.58*(99/(365*4+1)/(356*4+1))**0.5, 4)`, `r round(99/(365*4+1) + 2.58*(99/(365*4+1)/(356*4+1))**0.5, 4)`]**.


### After COVID-19  
The frequency table of DV after COVID-19 is as follows.

```{r}
DF_WM_20_21 <- DF_WM[DF_WM$Arrest_Year%in%c(2020,2021),]
DF_WM_20_21_DV <- DF_WM_20_21[DF_WM_20_21$Arrest_Category=='Offenses Against Family & Children',]

# table of date and the number of occurrences
DV_day_20_21 <- sapply(unique(DF_WM_20_21_DV$Arrest_Date),
                       function(x){sum(DF_WM_20_21_DV$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*2+1 - length(DV_day_20_21)`|`r (365*2+1 - length(DV_day_20_21))/(365*2+1)`|
|1|`r length(DV_day_20_21[DV_day_20_21==1])`|`r length(DV_day_20_21[DV_day_20_21==1])/(365*2+1)`|
|2|`r length(DV_day_20_21[DV_day_20_21==2])`|`r length(DV_day_20_21[DV_day_20_21==2])/(365*2+1)`|
|3|0|0|
|4|`r length(DV_day_20_21[DV_day_20_21==4])`|`r length(DV_day_20_21[DV_day_20_21==4])/(365*2+1)`|
|5|0|0|
|...|0|0|
|44|0|0|
|45|`r length(DV_day_20_21[DV_day_20_21==45])`|`r length(DV_day_20_21[DV_day_20_21==45])/(365*2+1)`|
|46|0|0|
|...|0|0|
|77|0|0|
|78|`r length(DV_day_20_21[DV_day_20_21==78])`|`r length(DV_day_20_21[DV_day_20_21==78])/(365*2+1)`|
|79|0|0|
|...|0|0|

There are two outliers (45 and 78) in the table. The dates of them are `r labels(DV_day_20_21[DV_day_20_21==45])` and `r labels(DV_day_20_21[DV_day_20_21==78])`. Since these dates are correspond to "Capitol attack" and "George Floyd protests", we will drop the value of these dates.  
  
The calculated $\lambda = 0.0725$. The histogram and the poisson distribution with $\lambda = 0.0725$ are shown in Figure 16.


```{r, fig.show="hold", out.width="48%"}
x_DV <- 0:5
y_DV <- c(680,47,1,0,1,0)
fx <- dpois(x=x_DV, lambda=53/(365*2+1))
data_DV <- data.frame(x_DV, y_DV, fx)

ggplot(data_DV, aes(x=x_DV,y=y_DV)) +
  ggtitle("Figure 15: Histogram of DV in 2020 - 2021") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_DV) +
  ggtitle("Figure 16: Reralive frequency histogram of DV in 2020 - 2021 \n and Pission distribution with lambda = 0.0725") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_DV,y=y_DV/(365*2+1)), stat = "identity") +
  geom_line(aes(x=x_DV,y=fx), color='red') +
  geom_point(aes(x=x_DV,y=fx), color='red')

```

The Poisson distribution fits well with the histogram.

**99% Confidence Interval of $\lambda$ for DV after COVID-19 is [`r round(53/(365*2+1) - 2.58*(53/(365*2+1)/(356*2+1))**0.5, 4)`, `r round(53/(365*2+1) + 2.58*(53/(365*2+1)/(356*2+1))**0.5, 4)`]**.

### Comparing Confidence Intervals

Figure 17 shows the Confidence Intervals before and after COVID-19. **There was overlap in the Confidence Intervals, and it is not possible to say that there was a change in the $\lambda$ of "Offenses Against Family & Children" before or after COVID-19**.

```{r}

x <- c('Before COVID-19','After COVID-19')
pre_covid_interval <- c(99/(365*4+1)-2.58*(99/(365*4+1)/(356*4+1))**0.5, 99/(365*4+1)+ 2.58*(99/(365*4+1)/(356*4+1))**0.5)
post_covid_interval <- c(53/(365*2+1) - 2.58*(53/(365*2+1)/(356*2+1))**0.5, 53/(365*2+1) + 2.58*(53/(365*2+1)/(356*2+1))**0.5)
data_CI_DV <- data.frame(x,pre_covid_interval,post_covid_interval)

ggplot(data_CI_DV) +
  ggtitle("Figure 17: 99% Confidence Interval of lambda for DV") + 
  xlab("") +
  ylab("99% Confidence Interval of lambda") + 
  coord_flip() +
  geom_linerange(aes(x=x[1], ymin=pre_covid_interval[1], ymax=pre_covid_interval[2])) +
  geom_linerange(aes(x=x[2], ymin=post_covid_interval[1], ymax=post_covid_interval[2]))
  

```


## Traffic Violations
### Before COVID-19
The trend of "Traffic Violations" also appears to have changed after COVID-19. The frequency table of Traffic Violations before COVID-19 is as follows.

```{r}
DF_WM_16_19_TV <- DF_WM_16_19[DF_WM_16_19$Arrest_Category=='Traffic Violations',]

# table of date and the number of occurrences
TV_day_16_19 <- sapply(unique(DF_WM_16_19_TV$Arrest_Date),
                       function(x){sum(DF_WM_16_19_TV$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*4+1 - length(TV_day_16_19)`|`r (365*4+1 - length(TV_day_16_19))/(365*4)`|
|1|`r length(TV_day_16_19[TV_day_16_19==1])`|`r length(TV_day_16_19[TV_day_16_19==1])/(365*4+1)`|
|2|`r length(TV_day_16_19[TV_day_16_19==2])`|`r length(TV_day_16_19[TV_day_16_19==2])/(365*4+1)`|
|3|`r length(TV_day_16_19[TV_day_16_19==3])`|`r length(TV_day_16_19[TV_day_16_19==3])/(365*4+1)`|
|4|`r length(TV_day_16_19[TV_day_16_19==4])`|`r length(TV_day_16_19[TV_day_16_19==4])/(365*4+1)`|
|5|`r length(TV_day_16_19[TV_day_16_19==5])`|`r length(TV_day_16_19[TV_day_16_19==5])/(365*4+1)`|
|6|`r length(TV_day_16_19[TV_day_16_19==6])`|`r length(TV_day_16_19[TV_day_16_19==6])/(365*4+1)`|
|7|0|0|

The calculated $\lambda = 0.907$. The histogram and the poisson distribution with $\lambda = 0.907$ are shown in Figure 19.

```{r, fig.show="hold", out.width="48%"}

x_TV <- 0:10
y_TV <- c(602,530,225,77,22,4,1,0,0,0,0)
fx <- dpois(x=x_TV, lambda=sum(TV_day_16_19)/(365*4+1))
data_TV <- data.frame(x_TV, y_TV, fx)

ggplot(data_TV, aes(x=x_TV,y=y_TV)) +
  ggtitle("Figure 18: Histogram of traffic violations in 2016 - 2019") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_TV) +
  ggtitle("Figure 19: Relative frequency histogram of traffic violations in 2016 - 2019 \n and Pission distribution with lambda = 0.907") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_TV,y=y_TV/(365*4+1)), stat = "identity") +
  geom_line(aes(x=x_TV,y=fx), color="red") +
  geom_point(aes(x=x_TV,y=fx), color='red')

```

The Poisson distribution fits well with the histogram.

**99% Confidence Interval of $\lambda$ for Traffic Violations before COVID-19 is [`r round(sum(TV_day_16_19)/(365*4+1) - 2.58*(sum(TV_day_16_19)/(365*4+1)/(356*4+1))**0.5, 3)`, `r round(sum(TV_day_16_19)/(365*4+1) + 2.58*(sum(TV_day_16_19)/(365*4+1)/(356*4+1))**0.5, 3)`]**.

### After COVID-19  
The frequency table of Traffic Violations after COVID-19 is as follows.

```{r}
DF_WM_20_21_TV <- DF_WM_20_21[DF_WM_20_21$Arrest_Category=='Traffic Violations',]

# table of date and the number of occurrences
TV_day_20_21 <- sapply(unique(DF_WM_20_21_TV$Arrest_Date),
                       function(x){sum(DF_WM_20_21_TV$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*2+1 - length(TV_day_20_21)`|`r (365*2+1 - length(TV_day_20_21))/(365*2+1)`|
|1|`r length(TV_day_20_21[TV_day_20_21==1])`|`r length(TV_day_20_21[TV_day_20_21==1])/(365*2+1)`|
|2|`r length(TV_day_20_21[TV_day_20_21==2])`|`r length(TV_day_20_21[TV_day_20_21==2])/(365*2+1)`|
|3|`r length(TV_day_20_21[TV_day_20_21==3])`|`r length(TV_day_20_21[TV_day_20_21==3])/(365*2+1)`|
|4|`r length(TV_day_20_21[TV_day_20_21==4])`|`r length(TV_day_20_21[TV_day_20_21==4])/(365*2+1)`|
|5|0|0|

The calculated $\lambda = 0.306$. The histogram and the poisson distribution with $\lambda = 0.306$ are shown in Figure 21.

```{r, fig.show="hold", out.width="48%"}

x_TV <- 0:10
y_TV <- c(546,156,23,3,3,0,0,0,0,0,0)
fx <- dpois(x=x_TV, lambda=sum(TV_day_20_21)/(365*2+1))
data_TV <- data.frame(x_TV, y_TV, fx)

ggplot(data_TV, aes(x=x_TV,y=y_TV)) +
  ggtitle("Figure 20: Histogram of traffic violations in 2020 - 2021") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_TV) +
  ggtitle("Figure 21: Relative frequency histogram of traffic violations in 2020 - 2021 \n and Pission distribution with lambda = 0.306") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_TV,y=y_TV/(365*2+1)), stat = "identity") +
  geom_line(aes(x=x_TV,y=fx), color="red") +
  geom_point(aes(x=x_TV,y=fx), color='red')

```

The Poisson distribution fits well with the histogram.

**99% Confidence Interval of $\lambda$ for Traffic Violations before COVID-19 is [`r round(sum(TV_day_20_21)/(365*2+1) - 2.58*(sum(TV_day_20_21)/(365*2+1)/(356*2+1))**0.5, 3)`, `r round(sum(TV_day_20_21)/(365*2+1) + 2.58*(sum(TV_day_20_21)/(365*2+1)/(356*2+1))**0.5, 3)`]**.

### Comparing Confidence Intervals

Figure 22 shows the Confidence Intervals before and after COVID-19. **There was no overlap in the Confidence Intervals, and there may have been a change in the Traffic Violations lambda before and after COVID-19**.

```{r}

x <- c('Before COVID-19','After COVID-19')
pre_covid_interval <- c(sum(TV_day_16_19)/(365*4+1) - 2.58*(sum(TV_day_16_19)/(365*4+1)/(356*4+1))**0.5,
                        sum(TV_day_16_19)/(365*4+1) + 2.58*(sum(TV_day_16_19)/(365*4+1)/(356*4+1))**0.5)
post_covid_interval <- c(sum(TV_day_20_21)/(365*2+1) - 2.58*(sum(TV_day_20_21)/(365*2+1)/(356*2+1))**0.5,
                         sum(TV_day_20_21)/(365*2+1) + 2.58*(sum(TV_day_20_21)/(365*2+1)/(356*2+1))**0.5)
data_CI_TV <- data.frame(x,pre_covid_interval,post_covid_interval)

ggplot(data_CI_TV) +
  ggtitle("Figure 22: 99% Confidence Interval of lambda for Traffic Violations") + 
  ylab("99% Confidence Interval of lambda") + 
  xlab("") +
  coord_flip() +
  geom_linerange(aes(x=x[1], ymin=pre_covid_interval[1], ymax=pre_covid_interval[2])) +
  geom_linerange(aes(x=x[2], ymin=post_covid_interval[1], ymax=post_covid_interval[2]))
  

```

## Simple Assault  
### Before COVID-19  
The below table shows the frequency and relative frequency of Simple Assault before COVID-19.

```{r}
DF_WM_16_19_SA <- DF_WM_16_19[DF_WM_16_19$Arrest_Category=='Simple Assault',]

# table of date and the number of occurrences
SA_day_16_19 <- sapply(unique(DF_WM_16_19_SA$Arrest_Date),
                       function(x){sum(DF_WM_16_19_SA$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*4+1 - length(SA_day_16_19)`|`r (365*4+1 - length(SA_day_16_19))/(365*4+1)`|
|1|`r length(SA_day_16_19[SA_day_16_19==1])`|`r length(SA_day_16_19[SA_day_16_19==1])/(365*4+1)`|
|2|`r length(SA_day_16_19[SA_day_16_19==2])`|`r length(SA_day_16_19[SA_day_16_19==2])/(365*4+1)`|
|3|`r length(SA_day_16_19[SA_day_16_19==3])`|`r length(SA_day_16_19[SA_day_16_19==3])/(365*4+1)`|
|4|`r length(SA_day_16_19[SA_day_16_19==4])`|`r length(SA_day_16_19[SA_day_16_19==4])/(365*4+1)`|
|5|`r length(SA_day_16_19[SA_day_16_19==5])`|`r length(SA_day_16_19[SA_day_16_19==5])/(365*4+1)`|
|6|`r length(SA_day_16_19[SA_day_16_19==6])`|`r length(SA_day_16_19[SA_day_16_19==6])/(365*4+1)`|
|7|`r length(SA_day_16_19[SA_day_16_19==7])`|`r length(SA_day_16_19[SA_day_16_19==7])/(365*4+1)`|
|8|`r length(SA_day_16_19[SA_day_16_19==8])`|`r length(SA_day_16_19[SA_day_16_19==8])/(365*4+1)`|
|9|`r length(SA_day_16_19[SA_day_16_19==9])`|`r length(SA_day_16_19[SA_day_16_19==9])/(365*4+1)`|
|10|`r length(SA_day_16_19[SA_day_16_19==10])`|`r length(SA_day_16_19[SA_day_16_19==10])/(365*4+1)`|

We got $\lambda = 1.36$ by calculating the average of occurrences per day.

```{r, fig.show="hold", out.width="48%"}

x_SA <- 0:10
y_SA <- c(438,479,284,156,76,13,8,4,1,2,0)
fx <- dpois(x=x_SA, lambda=sum(SA_day_16_19)/(365*4+1))
data_SA <- data.frame(x_SA, y_SA, fx)

ggplot(data_SA, aes(x=x_SA,y=y_SA)) +
  ggtitle("Figure 23: Histogram of Simple Assault in 2016 - 2019") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_SA) +
  ggtitle("Figure 24: Relative frequency histogram of Simple Assault in 2016 - 2019 \n and Poisson distribution with lambda = 1.36") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_SA,y=y_SA/(365*4+1)), stat = "identity") +
  geom_line(aes(x=x_SA,y=fx), color='red') +
  geom_point(aes(x=x_SA,y=fx), color='red')

```
  
### After COVID-19  
The frequency and relative frequency in 2020 and 2021 is shown in below. The $\lambda$ for 2020 and 2021 was $0.923$.
```{r}
DF_WM_20_21_SA <- DF_WM_20_21[DF_WM_20_21$Arrest_Category=='Simple Assault',]

# table of date and the number of occurrences
SA_day_20_21 <- sapply(unique(DF_WM_20_21_SA$Arrest_Date),
                       function(x){sum(DF_WM_20_21_SA$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*2+1 - length(SA_day_20_21)`|`r (365*2+1 - length(SA_day_20_21))/(365*2+1)`|
|1|`r length(SA_day_20_21[SA_day_20_21==1])`|`r length(SA_day_20_21[SA_day_20_21==1])/(365*2+1)`|
|2|`r length(SA_day_20_21[SA_day_20_21==2])`|`r length(SA_day_20_21[SA_day_20_21==2])/(365*2+1)`|
|3|`r length(SA_day_20_21[SA_day_20_21==3])`|`r length(SA_day_20_21[SA_day_20_21==3])/(365*2+1)`|
|4|`r length(SA_day_20_21[SA_day_20_21==4])`|`r length(SA_day_20_21[SA_day_20_21==4])/(365*2+1)`|
|5|`r length(SA_day_20_21[SA_day_20_21==5])`|`r length(SA_day_20_21[SA_day_20_21==5])/(365*2+1)`|
|6|`r length(SA_day_20_21[SA_day_20_21==6])`|`r length(SA_day_20_21[SA_day_20_21==6])/(365*2+1)`|
|7|`r length(SA_day_20_21[SA_day_20_21==7])`|`r length(SA_day_20_21[SA_day_20_21==7])/(365*2+1)`|
|8|`r length(SA_day_20_21[SA_day_20_21==8])`|`r length(SA_day_20_21[SA_day_20_21==8])/(365*2+1)`|
|9|`r length(SA_day_20_21[SA_day_20_21==9])`|`r length(SA_day_20_21[SA_day_20_21==9])/(365*2+1)`|


```{r, fig.show="hold", out.width="48%"}

x_SA <- 0:10
y_SA <- c(297,267,112,43,8,3,0,0,1,0,0)
fx <- dpois(x=x_SA, lambda=sum(SA_day_20_21)/(365*2+1))
data_SA <- data.frame(x_SA, y_SA, fx)

ggplot(data_SA, aes(x=x_SA,y=y_SA)) +
  ggtitle("Figure 25: Histogram of Simple Assault in 2020 - 2021") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_SA) +
  ggtitle("Figure 25: Relative frequency histogram of Simple Assault in 2020 - 2021 \n and Poisson distribution with lambda = 0.923") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_SA,y=y_SA/(365*2+1)), stat = "identity") +
  geom_line(aes(x=x_SA,y=fx), color='red') +
  geom_point(aes(x=x_SA,y=fx), color='red')

```
  
### Comparing Confidence Intervals  
Figure 26 shows the Confidence Intervals before and after COVID-19. **There was no overlap in the Confidence Intervals, and there may have been a change in the Simple Assault lambda before and after COVID-19**.
  
```{r}

x <- c('Before COVID-19','After COVID-19')
pre_covid_interval <- c(sum(SA_day_16_19)/(365*4+1) - 2.58*(sum(SA_day_16_19)/(365*4+1)/(356*4+1))**0.5,
                        sum(SA_day_16_19)/(365*4+1) + 2.58*(sum(SA_day_16_19)/(365*4+1)/(356*4+1))**0.5)
post_covid_interval <- c(sum(SA_day_20_21)/(365*2+1) - 2.58*(sum(SA_day_20_21)/(365*2+1)/(356*2+1))**0.5,
                         sum(SA_day_20_21)/(365*2+1) + 2.58*(sum(SA_day_20_21)/(365*2+1)/(356*2+1))**0.5)
data_CI_SA <- data.frame(x,pre_covid_interval,post_covid_interval)

ggplot(data_CI_SA) +
  ggtitle("Figure 26: 99% Confidence Interval of lambda for Simple Assault") + 
  ylab("99% Confidence Interval of lambda") + 
  xlab("") +
  coord_flip() +
  geom_linerange(aes(x=x[1], ymin=pre_covid_interval[1], ymax=pre_covid_interval[2])) +
  geom_linerange(aes(x=x[2], ymin=post_covid_interval[1], ymax=post_covid_interval[2]))
  

```

## Theft  
### Before COVID-19  
The frequency and relative frequency in 2016 to 2019 is shown in below. The $\lambda$ before COVID-19 was $0.404$.

```{r}
DF_WM_16_19_T <- DF_WM_16_19[DF_WM_16_19$Arrest_Category=='Theft',]

# table of date and the number of occurrences
T_day_16_19 <- sapply(unique(DF_WM_16_19_T$Arrest_Date),
                       function(x){sum(DF_WM_16_19_T$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*4+1 - length(T_day_16_19)`|`r (365*4+1 - length(T_day_16_19))/(365*4+1)`|
|1|`r length(T_day_16_19[T_day_16_19==1])`|`r length(T_day_16_19[T_day_16_19==1])/(365*4+1)`|
|2|`r length(T_day_16_19[T_day_16_19==2])`|`r length(T_day_16_19[T_day_16_19==2])/(365*4+1)`|
|3|`r length(T_day_16_19[T_day_16_19==3])`|`r length(T_day_16_19[T_day_16_19==3])/(365*4+1)`|
|4|`r length(T_day_16_19[T_day_16_19==4])`|`r length(T_day_16_19[T_day_16_19==4])/(365*4+1)`|
|5|`r length(T_day_16_19[T_day_16_19==5])`|`r length(T_day_16_19[T_day_16_19==5])/(365*4+1)`|

```{r, fig.show="hold", out.width="48%"}

x_T <- 0:5
y_T <- c(973,398,79,10,1,0)
fx <- dpois(x=x_T, lambda=sum(T_day_16_19)/(365*4+1))
data_T <- data.frame(x_T, y_T, fx)

ggplot(data_T, aes(x=x_T,y=y_T)) +
  ggtitle("Figure 27: Histogram of Theft in 2016 - 2019") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_T) +
  ggtitle("Figure 28: Relative frequency histogram of Theft in 2016 - 2019 \n and Poisson distribution with lambda = 0.404") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_T,y=y_T/(365*4+1)), stat = "identity") +
  geom_line(aes(x=x_T,y=fx), color='red') +
  geom_point(aes(x=x_T,y=fx), color='red')

```
  
### After COVID-19  
The frequency and relative frequency in 2020 and 2021 are shown in below. The $\lambda$ for 2020 and 2021 was $0.115$.
  
```{r}
DF_WM_20_21_T <- DF_WM_20_21[DF_WM_20_21$Arrest_Category=='Theft',]

# table of date and the number of occurrences
T_day_20_21 <- sapply(unique(DF_WM_20_21_T$Arrest_Date),
                       function(x){sum(DF_WM_20_21_T$Arrest_Date==x)})
```


| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*2+1 - length(T_day_20_21)`|`r (365*2+1 - length(T_day_20_21))/(365*2+1)`|
|1|`r length(T_day_20_21[T_day_20_21==1])`|`r length(T_day_20_21[T_day_20_21==1])/(365*2+1)`|
|2|`r length(T_day_20_21[T_day_20_21==2])`|`r length(T_day_20_21[T_day_20_21==2])/(365*2+1)`|
|3|`r length(T_day_20_21[T_day_20_21==3])`|`r length(T_day_20_21[T_day_20_21==3])/(365*2+1)`|

```{r, fig.show="hold", out.width="48%"}

x_T <- 0:3
y_T <- c(653,72,6,0)
fx <- dpois(x=x_T, lambda=sum(T_day_20_21)/(365*2+1))
data_T <- data.frame(x_T, y_T, fx)

ggplot(data_T, aes(x=x_T,y=y_T)) +
  ggtitle("Figure 29: Histogram of Theft in 2020 - 2021") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_T) +
  ggtitle("Figure 30: Relative frequency histogram of Theft in 2020 - 2021 \n and Poisson distribution with lambda = 0.115") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_T,y=y_T/(365*2+1)), stat = "identity") +
  geom_line(aes(x=x_T,y=fx), color='red') +
  geom_point(aes(x=x_T,y=fx), color='red')

```
  
### Comparing Confidence Intervals  
Figure 31 shows the Confidence Intervals before and after COVID-19. **There was no overlap in the Confidence Intervals, and there may have been a change in the Theft lambda before and after COVID-19**.
  
```{r}

x <- c('Before COVID-19','After COVID-19')
pre_covid_interval <- c(sum(T_day_16_19)/(365*4+1) - 2.58*(sum(T_day_16_19)/(365*4+1)/(356*4+1))**0.5,
                        sum(T_day_16_19)/(365*4+1) + 2.58*(sum(T_day_16_19)/(365*4+1)/(356*4+1))**0.5)
post_covid_interval <- c(sum(T_day_20_21)/(365*2+1) - 2.58*(sum(T_day_20_21)/(365*2+1)/(356*2+1))**0.5,
                         sum(T_day_20_21)/(365*2+1) + 2.58*(sum(T_day_20_21)/(365*2+1)/(356*2+1))**0.5)
data_CI_T <- data.frame(x,pre_covid_interval,post_covid_interval)

ggplot(data_CI_T) +
  ggtitle("Figure 31: 99% Confidence Interval of lambda for Theft") + 
  ylab("99% Confidence Interval of lambda") + 
  xlab("") +
  coord_flip() +
  geom_linerange(aes(x=x[1], ymin=pre_covid_interval[1], ymax=pre_covid_interval[2])) +
  geom_linerange(aes(x=x[2], ymin=post_covid_interval[1], ymax=post_covid_interval[2]))
  

```

  
# Interpretation  
## Simple Assault and Traffic Violations
Statistically significant reductions in Simple Assault and Traffic Violations were observed for $\lambda$ before and after COVID-19. Since these crimes seem to be more likely to occur the more people are out, it is likely that the restrictions and curbs on going out due to COVID-19 contributed to the decrease in these crimes.  

## Theft
A statistically significant decrease in theft was also observed in $\lambda$ before and after Corona. Considering that thefts are committed against empty homes, the decrease in empty homes due to the curfew restrictions caused by COVID-19 may have contributed to the decrease in thefts.

## Offenses Against Family & Children  
The more time one spends at home due, the more Offenses Against Family & Children are likely to increase. In fact, in terms of the number of cases alone, Offenses Against Family & Children have increased after COVID-19. At first glance, the curfew restrictions caused by COVID-19 seems to be the cause. However, most of these cases were caused by special incidents unrelated to COVID-19, and when these effects were removed, there was no statistically significant difference in the change in Offenses Against Family & Children before and after COVID-19. As for white males in the DC area, Offenses Against Family & Children to the point of arrest does not appear to be affected by the changes in their lives caused by COVID-19.



# Appendix - Other Major Crimes
## Release Violations/Fugitive  
### Before COVID-19
```{r}
DF_WM_16_19_RV <- DF_WM_16_19[DF_WM_16_19$Arrest_Category=='Release Violations/Fugitive',]

# table of date and the number of occurrences
RV_day_16_19 <- sapply(unique(DF_WM_16_19_RV$Arrest_Date),
                       function(x){sum(DF_WM_16_19_RV$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*4+1 - length(RV_day_16_19)`|`r (365*4+1 - length(RV_day_16_19))/(365*4+1)`|
|1|`r length(RV_day_16_19[RV_day_16_19==1])`|`r length(RV_day_16_19[RV_day_16_19==1])/(365*4+1)`|
|2|`r length(RV_day_16_19[RV_day_16_19==2])`|`r length(RV_day_16_19[RV_day_16_19==2])/(365*4+1)`|
|3|`r length(RV_day_16_19[RV_day_16_19==3])`|`r length(RV_day_16_19[RV_day_16_19==3])/(365*4+1)`|
|4|`r length(RV_day_16_19[RV_day_16_19==4])`|`r length(RV_day_16_19[RV_day_16_19==4])/(365*4+1)`|
|5|`r length(RV_day_16_19[RV_day_16_19==5])`|`r length(RV_day_16_19[RV_day_16_19==5])/(365*4+1)`|
|6|`r length(RV_day_16_19[RV_day_16_19==6])`|`r length(RV_day_16_19[RV_day_16_19==6])/(365*4+1)`|

```{r, fig.show="hold", out.width="48%"}

x_RV <- 0:6
y_RV <- c(817,428,168,40,5,3,0)
fx <- dpois(x=x_RV, lambda=sum(RV_day_16_19)/(365*4+1))
data_RV <- data.frame(x_RV, y_RV, fx)

ggplot(data_RV, aes(x=x_RV,y=y_RV)) +
  ggtitle("Figure : Histogram of Release Violations/Fugitive in 2016 - 2019") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_RV) +
  ggtitle("Figure : Relative frequency histogram of Release Violations/Fugitive in 2016 - 2019 \n and Poisson distribution with lambda = 0.629") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_RV,y=y_RV/(365*4+1)), stat = "identity") +
  geom_line(aes(x=x_RV,y=fx), color='red') +
  geom_point(aes(x=x_RV,y=fx), color='red')

```
  
### After COVID-19
  
```{r}
DF_WM_20_21_RV <- DF_WM_20_21[DF_WM_20_21$Arrest_Category=='Release Violations/Fugitive',]

# table of date and the number of occurrences
RV_day_20_21 <- sapply(unique(DF_WM_20_21_RV$Arrest_Date),
                       function(x){sum(DF_WM_20_21_RV$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*2+1 - length(RV_day_20_21)`|`r (365*2+1 - length(RV_day_20_21))/(365*2+1)`|
|1|`r length(RV_day_20_21[RV_day_20_21==1])`|`r length(RV_day_20_21[RV_day_20_21==1])/(365*2+1)`|
|2|`r length(RV_day_20_21[RV_day_20_21==2])`|`r length(RV_day_20_21[RV_day_20_21==2])/(365*2+1)`|
|3|`r length(RV_day_20_21[RV_day_20_21==3])`|`r length(RV_day_20_21[RV_day_20_21==3])/(365*2+1)`|
|4|`r length(RV_day_20_21[RV_day_20_21==4])`|`r length(RV_day_20_21[RV_day_20_21==4])/(365*2+1)`|

```{r, fig.show="hold", out.width="48%"}

x_RV <- 0:4
y_RV <- c(549,154,24,4,0)
fx <- dpois(x=x_RV, lambda=sum(RV_day_20_21)/(365*2+1))
data_RV <- data.frame(x_RV, y_RV, fx)

ggplot(data_RV, aes(x=x_RV,y=y_RV)) +
  ggtitle("Figure : Histogram of Release Violations/Fugitive in 2020 - 2021") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_RV) +
  ggtitle("Figure : Relative frequency histogram of Release Violations/Fugitive in 2020 - 2021 \n and Poisson distribution with lambda = 0.293") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_RV,y=y_RV/(365*2+1)), stat = "identity") +
  geom_line(aes(x=x_RV,y=fx), color='red') +
  geom_point(aes(x=x_RV,y=fx), color='red')

```
  
### Comparing Confidence Intervals
  
```{r}

x <- c('Before COVID-19','After COVID-19')
pre_covid_interval <- c(sum(RV_day_16_19)/(365*4+1) - 2.58*(sum(RV_day_16_19)/(365*4+1)/(356*4+1))**0.5,
                        sum(RV_day_16_19)/(365*4+1) + 2.58*(sum(RV_day_16_19)/(365*4+1)/(356*4+1))**0.5)
post_covid_interval <- c(sum(RV_day_20_21)/(365*2+1) - 2.58*(sum(RV_day_20_21)/(365*2+1)/(356*2+1))**0.5,
                         sum(RV_day_20_21)/(365*2+1) + 2.58*(sum(RV_day_20_21)/(365*2+1)/(356*2+1))**0.5)
data_CI_RV <- data.frame(x,pre_covid_interval,post_covid_interval)

ggplot(data_CI_RV) +
  ggtitle("Figure : 99% Confidence Interval of lambda for Release Violations/Fugitive") + 
  ylab("99% Confidence Interval of lambda") + 
  xlab("") +
  coord_flip() +
  geom_linerange(aes(x=x[1], ymin=pre_covid_interval[1], ymax=pre_covid_interval[2])) +
  geom_linerange(aes(x=x[2], ymin=post_covid_interval[1], ymax=post_covid_interval[2]))
  

```

## Driving/Boating While Intoxicated  
### Before COVID-19  

```{r}
DF_WM_16_19_DI <- DF_WM_16_19[DF_WM_16_19$Arrest_Category=='Driving/Boating While Intoxicated',]

# table of date and the number of occurrences
DI_day_16_19 <- sapply(unique(DF_WM_16_19_DI$Arrest_Date),
                       function(x){sum(DF_WM_16_19_DI$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*4+1 - length(DI_day_16_19)`|`r (365*4+1 - length(DI_day_16_19))/(365*4+1)`|
|1|`r length(DI_day_16_19[DI_day_16_19==1])`|`r length(DI_day_16_19[DI_day_16_19==1])/(365*4+1)`|
|2|`r length(DI_day_16_19[DI_day_16_19==2])`|`r length(DI_day_16_19[DI_day_16_19==2])/(365*4+1)`|
|3|`r length(DI_day_16_19[DI_day_16_19==3])`|`r length(DI_day_16_19[DI_day_16_19==3])/(365*4+1)`|
|4|`r length(DI_day_16_19[DI_day_16_19==4])`|`r length(DI_day_16_19[DI_day_16_19==4])/(365*4+1)`|
|5|`r length(DI_day_16_19[DI_day_16_19==5])`|`r length(DI_day_16_19[DI_day_16_19==5])/(365*4+1)`|
|6|`r length(DI_day_16_19[DI_day_16_19==6])`|`r length(DI_day_16_19[DI_day_16_19==6])/(365*4+1)`|
  
  
```{r, fig.show="hold", out.width="48%"}

x_DI <- 0:6
y_DI <- c(875,416,138,25,6,1,0)
fx <- dpois(x=x_DI, lambda=sum(DI_day_16_19)/(365*4+1))
data_DI <- data.frame(x_DI, y_DI, fx)

ggplot(data_DI, aes(x=x_DI,y=y_DI)) +
  ggtitle("Figure : Histogram of Driving/Boating While Intoxicated in 2016 - 2019") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_DI) +
  ggtitle("Figure : Relative frequency histogram of Driving/Boating While Intoxicated in 2016 - 2019 \n and Poisson distribution with lambda = 0.545") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_DI,y=y_DI/(365*4+1)), stat = "identity") +
  geom_line(aes(x=x_DI,y=fx), color='red') +
  geom_point(aes(x=x_DI,y=fx), color='red')

```
  
### After COVID-19
  
```{r}
DF_WM_20_21_DI <- DF_WM_20_21[DF_WM_20_21$Arrest_Category=='Driving/Boating While Intoxicated',]

# table of date and the number of occurrences
DI_day_20_21 <- sapply(unique(DF_WM_20_21_DI$Arrest_Date),
                       function(x){sum(DF_WM_20_21_DI$Arrest_Date==x)})
```


| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*2+1 - length(DI_day_20_21)`|`r (365*2+1 - length(DI_day_20_21))/(365*2+1)`|
|1|`r length(DI_day_20_21[DI_day_20_21==1])`|`r length(DI_day_20_21[DI_day_20_21==1])/(365*2+1)`|
|2|`r length(DI_day_20_21[DI_day_20_21==2])`|`r length(DI_day_20_21[DI_day_20_21==2])/(365*2+1)`|
|3|`r length(DI_day_20_21[DI_day_20_21==3])`|`r length(DI_day_20_21[DI_day_20_21==3])/(365*2+1)`|
|4|`r length(DI_day_20_21[DI_day_20_21==4])`|`r length(DI_day_20_21[DI_day_20_21==4])/(365*2+1)`|
|5|`r length(DI_day_20_21[DI_day_20_21==5])`|`r length(DI_day_20_21[DI_day_20_21==5])/(365*2+1)`|


```{r, fig.show="hold", out.width="48%"}

x_DI <- 0:5
y_DI <- c(527,168,29,5,2,0)
fx <- dpois(x=x_DI, lambda=sum(DI_day_20_21)/(365*2+1))
data_DI <- data.frame(x_DI, y_DI, fx)

ggplot(data_DI, aes(x=x_DI,y=y_DI)) +
  ggtitle("Figure : Histogram of Driving/Boating While Intoxicated in 2020 - 2021") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_DI) +
  ggtitle("Figure : Relative frequency histogram of Driving/Boating While Intoxicated in 2020 - 2021 \n and Poisson distribution with lambda = 0.341") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_DI,y=y_DI/(365*2+1)), stat = "identity") +
  geom_line(aes(x=x_DI,y=fx), color='red') +
  geom_point(aes(x=x_DI,y=fx), color='red')

```
  
### Comparing Confidence Intervals
  
```{r}

x <- c('Before COVID-19','After COVID-19')
pre_covid_interval <- c(sum(DI_day_16_19)/(365*4+1) - 2.58*(sum(DI_day_16_19)/(365*4+1)/(356*4+1))**0.5,
                        sum(DI_day_16_19)/(365*4+1) + 2.58*(sum(DI_day_16_19)/(365*4+1)/(356*4+1))**0.5)
post_covid_interval <- c(sum(DI_day_20_21)/(365*2+1) - 2.58*(sum(DI_day_20_21)/(365*2+1)/(356*2+1))**0.5,
                         sum(DI_day_20_21)/(365*2+1) + 2.58*(sum(DI_day_20_21)/(365*2+1)/(356*2+1))**0.5)
data_CI_DI <- data.frame(x,pre_covid_interval,post_covid_interval)

ggplot(data_CI_DI) +
  ggtitle("Figure : 99% Confidence Interval of lambda for Driving/Boating While Intoxicated") + 
  ylab("99% Confidence Interval of lambda") + 
  xlab("") +
  coord_flip() +
  geom_linerange(aes(x=x[1], ymin=pre_covid_interval[1], ymax=pre_covid_interval[2])) +
  geom_linerange(aes(x=x[2], ymin=post_covid_interval[1], ymax=post_covid_interval[2]))
  

```

## Narcotics  
### Before COVID-19  

```{r}
DF_WM_16_19_N <- DF_WM_16_19[DF_WM_16_19$Arrest_Category=='Narcotics',]

# table of date and the number of occurrences
N_day_16_19 <- sapply(unique(DF_WM_16_19_N$Arrest_Date),
                       function(x){sum(DF_WM_16_19_N$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*4+1 - length(N_day_16_19)`|`r (365*4+1 - length(N_day_16_19))/(365*4+1)`|
|1|`r length(N_day_16_19[N_day_16_19==1])`|`r length(N_day_16_19[N_day_16_19==1])/(365*4+1)`|
|2|`r length(N_day_16_19[N_day_16_19==2])`|`r length(N_day_16_19[N_day_16_19==2])/(365*4+1)`|
|3|`r length(N_day_16_19[N_day_16_19==3])`|`r length(N_day_16_19[N_day_16_19==3])/(365*4+1)`|
|4|`r length(N_day_16_19[N_day_16_19==4])`|`r length(N_day_16_19[N_day_16_19==4])/(365*4+1)`|
|5|`r length(N_day_16_19[N_day_16_19==5])`|`r length(N_day_16_19[N_day_16_19==5])/(365*4+1)`|
|6|`r length(N_day_16_19[N_day_16_19==6])`|`r length(N_day_16_19[N_day_16_19==6])/(365*4+1)`|
|7|`r length(N_day_16_19[N_day_16_19==7])`|`r length(N_day_16_19[N_day_16_19==7])/(365*4+1)`|
|8|`r length(N_day_16_19[N_day_16_19==8])`|`r length(N_day_16_19[N_day_16_19==8])/(365*4+1)`|
|9|`r length(N_day_16_19[N_day_16_19==9])`|`r length(N_day_16_19[N_day_16_19==9])/(365*4+1)`|
|10|`r length(N_day_16_19[N_day_16_19==10])`|`r length(N_day_16_19[N_day_16_19==10])/(365*4+1)`|
|11|`r length(N_day_16_19[N_day_16_19==11])`|`r length(N_day_16_19[N_day_16_19==11])/(365*4+1)`|
|12|`r length(N_day_16_19[N_day_16_19==12])`|`r length(N_day_16_19[N_day_16_19==12])/(365*4+1)`|
|13|`r length(N_day_16_19[N_day_16_19==13])`|`r length(N_day_16_19[N_day_16_19==13])/(365*4+1)`|
|14|`r length(N_day_16_19[N_day_16_19==14])`|`r length(N_day_16_19[N_day_16_19==14])/(365*4+1)`|

```{r, fig.show="hold", out.width="48%"}

x_N <- 0:14
y_N <- c(1053,318,66,10,5,6,0,1,0,1,0,0,0,1,0)
fx <- dpois(x=x_N, lambda=sum(N_day_16_19)/(365*4+1))
data_N <- data.frame(x_N, y_N, fx)

ggplot(data_N, aes(x=x_N,y=y_N)) +
  ggtitle("Figure : Histogram of Narcotics in 2016 - 2019") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_N) +
  ggtitle("Figure : Relative frequency histogram of Narcotics in 2016 - 2019 \n and Poisson distribution with lambda = 0.383") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_N,y=y_N/(365*4+1)), stat = "identity") +
  geom_line(aes(x=x_N,y=fx), color='red') +
  geom_point(aes(x=x_N,y=fx), color='red')

```
  
### After COVID-19
  
```{r}
DF_WM_20_21_N <- DF_WM_20_21[DF_WM_20_21$Arrest_Category=='Narcotics',]

# table of date and the number of occurrences
N_day_20_21 <- sapply(unique(DF_WM_20_21_N$Arrest_Date),
                       function(x){sum(DF_WM_20_21_N$Arrest_Date==x)})
```


| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*2+1 - length(N_day_20_21)`|`r (365*2+1 - length(N_day_20_21))/(365*2+1)`|
|1|`r length(N_day_20_21[N_day_20_21==1])`|`r length(N_day_20_21[N_day_20_21==1])/(365*2+1)`|
|2|`r length(N_day_20_21[N_day_20_21==2])`|`r length(N_day_20_21[N_day_20_21==2])/(365*2+1)`|
|3|`r length(N_day_20_21[N_day_20_21==3])`|`r length(N_day_20_21[N_day_20_21==3])/(365*2+1)`|
|4|`r length(N_day_20_21[N_day_20_21==4])`|`r length(N_day_20_21[N_day_20_21==4])/(365*2+1)`|


```{r, fig.show="hold", out.width="48%"}

x_N <- 0:4
y_N <- c(652,66,10,3,0)
fx <- dpois(x=x_N, lambda=sum(N_day_20_21)/(365*2+1))
data_N <- data.frame(x_N, y_N, fx)

ggplot(data_N, aes(x=x_N,y=y_N)) +
  ggtitle("Figure : Histogram of Narcotics in 2020 - 2021") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_N) +
  ggtitle("Figure : Relative frequency histogram of Narcotics in 2020 - 2021 \n and Poisson distribution with lambda = 0.13") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_N,y=y_N/(365*2+1)), stat = "identity") +
  geom_line(aes(x=x_N,y=fx), color='red') +
  geom_point(aes(x=x_N,y=fx), color='red')

```
  
### Comparing Confidence Intervals
  
```{r}

x <- c('Before COVID-19','After COVID-19')
pre_covid_interval <- c(sum(N_day_16_19)/(365*4+1) - 2.58*(sum(N_day_16_19)/(365*4+1)/(356*4+1))**0.5,
                        sum(N_day_16_19)/(365*4+1) + 2.58*(sum(N_day_16_19)/(365*4+1)/(356*4+1))**0.5)
post_covid_interval <- c(sum(N_day_20_21)/(365*2+1) - 2.58*(sum(N_day_20_21)/(365*2+1)/(356*2+1))**0.5,
                         sum(N_day_20_21)/(365*2+1) + 2.58*(sum(N_day_20_21)/(365*2+1)/(356*2+1))**0.5)
data_CI_N <- data.frame(x,pre_covid_interval,post_covid_interval)

ggplot(data_CI_N) +
  ggtitle("Figure : 99% Confidence Interval of lambda for Narcotics") + 
  ylab("99% Confidence Interval of lambda") + 
  xlab("") +
  coord_flip() +
  geom_linerange(aes(x=x[1], ymin=pre_covid_interval[1], ymax=pre_covid_interval[2])) +
  geom_linerange(aes(x=x[2], ymin=post_covid_interval[1], ymax=post_covid_interval[2]))
  

```

## Liquor Law Violations  
### Before COVID-19

```{r}
DF_WM_16_19_LV <- DF_WM_16_19[DF_WM_16_19$Arrest_Category=='Liquor Law Violations',]

# table of date and the number of occurrences
LV_day_16_19 <- sapply(unique(DF_WM_16_19_LV$Arrest_Date),
                       function(x){sum(DF_WM_16_19_LV$Arrest_Date==x)})
```

| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*4+1 - length(LV_day_16_19)`|`r (365*4+1 - length(LV_day_16_19))/(365*4+1)`|
|1|`r length(LV_day_16_19[LV_day_16_19==1])`|`r length(LV_day_16_19[LV_day_16_19==1])/(365*4+1)`|
|2|`r length(LV_day_16_19[LV_day_16_19==2])`|`r length(LV_day_16_19[LV_day_16_19==2])/(365*4+1)`|
|3|`r length(LV_day_16_19[LV_day_16_19==3])`|`r length(LV_day_16_19[LV_day_16_19==3])/(365*4+1)`|
|4|`r length(LV_day_16_19[LV_day_16_19==4])`|`r length(LV_day_16_19[LV_day_16_19==4])/(365*4+1)`|
|5|`r length(LV_day_16_19[LV_day_16_19==5])`|`r length(LV_day_16_19[LV_day_16_19==5])/(365*4+1)`|
|6|`r length(LV_day_16_19[LV_day_16_19==6])`|`r length(LV_day_16_19[LV_day_16_19==6])/(365*4+1)`|

```{r, fig.show="hold", out.width="48%"}

x_LV <- 0:6
y_LV <- c(1090,259,76,32,3,1,0)
fx <- dpois(x=x_LV, lambda=sum(LV_day_16_19)/(365*4+1))
data_LV <- data.frame(x_LV, y_LV, fx)

ggplot(data_LV, aes(x=x_LV,y=y_LV)) +
  ggtitle("Figure : Histogram of Liquor Law Violations in 2016 - 2019") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_LV) +
  ggtitle("Figure : Relative frequency histogram of Liquor Law Violations in 2016 - 2019 \n and Poisson distribution with lambda = 0.359") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_LV,y=y_LV/(365*4+1)), stat = "identity") +
  geom_line(aes(x=x_LV,y=fx), color='red') +
  geom_point(aes(x=x_LV,y=fx), color='red')

```
  
### After COVID-19
  
```{r}
DF_WM_20_21_LV <- DF_WM_20_21[DF_WM_20_21$Arrest_Category=='Liquor Law Violations',]

# table of date and the number of occurrences
LV_day_20_21 <- sapply(unique(DF_WM_20_21_LV$Arrest_Date),
                       function(x){sum(DF_WM_20_21_LV$Arrest_Date==x)})
```


| # of occurrences per day | Frequency | Relative frequency |
|:------------------------:|:---------:|:------------------:|
|0|`r 365*2+1 - length(LV_day_20_21)`|`r (365*2+1 - length(LV_day_20_21))/(365*2+1)`|
|1|`r length(LV_day_20_21[LV_day_20_21==1])`|`r length(LV_day_20_21[LV_day_20_21==1])/(365*2+1)`|
|2|`r length(LV_day_20_21[LV_day_20_21==2])`|`r length(LV_day_20_21[LV_day_20_21==2])/(365*2+1)`|
|3|`r length(LV_day_20_21[LV_day_20_21==3])`|`r length(LV_day_20_21[LV_day_20_21==3])/(365*2+1)`|
|4|`r length(LV_day_20_21[LV_day_20_21==4])`|`r length(LV_day_20_21[LV_day_20_21==4])/(365*2+1)`|


```{r, fig.show="hold", out.width="48%"}

x_LV <- 0:4
y_LV <- c(699,27,4,1,0)
fx <- dpois(x=x_LV, lambda=sum(LV_day_20_21)/(365*2+1))
data_LV <- data.frame(x_LV, y_LV, fx)

ggplot(data_LV, aes(x=x_LV,y=y_LV)) +
  ggtitle("Figure : Histogram of Liquor Law Violations in 2020 - 2021") + 
  xlab("Number of occurrences per day") + 
  ylab("Frequency") +
  geom_bar(stat = "identity") 

ggplot(data_LV) +
  ggtitle("Figure : Relative frequency histogram of Liquor Law Violations in 2020 - 2021 \n and Poisson distribution with lambda = 0.052") + 
  xlab("Number of occurrences per day") + 
  ylab("Relative frequency") +
  geom_bar(aes(x=x_LV,y=y_LV/(365*2+1)), stat = "identity") +
  geom_line(aes(x=x_LV,y=fx), color='red') +
  geom_point(aes(x=x_LV,y=fx), color='red')

```
  
### Comparing Confidence Intervals
  
```{r}

x <- c('Before COVID-19','After COVID-19')
pre_covid_interval <- c(sum(LV_day_16_19)/(365*4+1) - 2.58*(sum(LV_day_16_19)/(365*4+1)/(356*4+1))**0.5,
                        sum(LV_day_16_19)/(365*4+1) + 2.58*(sum(LV_day_16_19)/(365*4+1)/(356*4+1))**0.5)
post_covid_interval <- c(sum(LV_day_20_21)/(365*2+1) - 2.58*(sum(LV_day_20_21)/(365*2+1)/(356*2+1))**0.5,
                         sum(LV_day_20_21)/(365*2+1) + 2.58*(sum(LV_day_20_21)/(365*2+1)/(356*2+1))**0.5)
data_CI_LV <- data.frame(x,pre_covid_interval,post_covid_interval)

ggplot(data_CI_LV) +
  ggtitle("Figure : 99% Confidence Interval of lambda for Liquor Law Violations") + 
  ylab("99% Confidence Interval of lambda") + 
  xlab("") +
  coord_flip() +
  geom_linerange(aes(x=x[1], ymin=pre_covid_interval[1], ymax=pre_covid_interval[2])) +
  geom_linerange(aes(x=x[2], ymin=post_covid_interval[1], ymax=post_covid_interval[2]))
  

```








